### 2019-09-04 paper/paper.tex
Update template to be usable

% Template taken from https://www.sharelatex.com/templates/journals/template-for-the-journal-of-machine-learning-research-jmlr

\documentclass[twoside,11pt]{article}

% Any additional packages needed should be included after jmlr2e.
% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
% and defines many common macros, such as 'proof' and 'example'.
%
% It also sets the bibliographystyle to plainnat; for more information on
% natbib citation styles, see the natbib documentation, a copy of which
% is archived at http://www.jmlr.org/format/natbib.pdf

\usepackage{jmlr2e}

% Definitions of handy macros can go here

\newcommand{\dataset}{{\cal D}}
\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}

% Heading arguments are {volume}{year}{pages}{submitted}{published}{author-full-names}

\jmlrheading{1}{2000}{1-48}{4/00}{10/00}{Marina Meil\u{a} and Michael I. Jordan}

% Short headings should be running head and authors last names

\ShortHeadings{CSCI 447: Project 1}{Engel, Oster, Parker, Soule}
\firstpageno{1}

\begin{document}

\title{CSCI 447: Project 1}

\author{\name George Engel \email GeoEngel.z@gmail.com \\
       \addr Department of Engineering\\
       Montana State University\\
       Bozemane, MT 59715, USA
       \AND
       \name Troy Oster \email toster1011@gmail.com \\
       \addr Department of Engineering\\
       Montana State University\\
       Bozeman, MT 59715, USA
       \AND
       \name Dana Parker \email danaharmonparker@gmail.com \\
       \addr Department of Engineering\\
       Montana State University\\
       Bozeman, MT 59715, USA
       \AND
       \name Henry Soule \email hsoule427@gmail.com \\
       \addr Department of Engineering\\
       Montana State University\\
       Bozeman, MT 59715, USA}

\editor{}

\maketitle

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file

Text goes here.
% Original text:
% This paper describes the mixtures-of-trees model, a probabilistic 
% model for discrete multidimensional domains.  Mixtures-of-trees 
% generalize the probabilistic trees of \citet{chow:68}
% in a different and complementary direction to that of Bayesian networks.
% We present efficient algorithms for learning mixtures-of-trees 
% models in maximum likelihood and Bayesian frameworks. 
% We also discuss additional efficiencies that can be
% obtained when data are ``sparse,'' and we present data 
% structures and algorithms that exploit such sparseness.
% Experimental results demonstrate the performance of the 
% model for both density estimation and classification. 
% We also discuss the sense in which tree-based classifiers
% perform an implicit form of feature selection, and demonstrate
% a resulting insensitivity to irrelevant attributes.
\end{abstract}

\begin{keywords}
    Keywords, Go, Here
%   Bayesian Networks, Mixture Models, Chow-Liu Trees
\end{keywords}

\section{Introduction}

Intro goes here.

% Acknowledgements should go at the end, before appendices and references

\acks{Acknowledgements go here.}

% \acks{We would like to acknowledge support for this project
% from the National Science Foundation (NSF grant IIS-9988642)
% and the Multidisciplinary Research Program of the Department
% of Defense (MURI N00014-00-1-0637). }

% Manual newpage inserted to improve layout of sample file - not
% needed in general before appendices/bibliography.

\newpage

\appendix
\section*{Appendix A.}
\label{app:theorem}

% Note: in this sample, the section number is hard-coded in. Following
% proper LaTeX conventions, it should properly be coded as a reference:

%In this appendix we prove the following theorem from
%Section~\ref{sec:textree-generalization}:

In this appendix we prove the following theorem from
Section~6.2:

\noindent
{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
respective empirical mutual information values based on the sample
$\dataset$. Then
\[
	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
\]
with equality only if $u$ is identically 0.} \hfill\BlackBox

\noindent
{\bf Proof}. We use the notation:
\[
P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
\]
These values represent the (empirical) probabilities of $v$
taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\

{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}

\vskip 0.2in
\bibliography{sample}

\end{document}

### 2019-09-04 Driver.py
Added data correction method which currently just removes unfinished set

@@ -1,6 +1,7 @@
 import processData
 
 print("Starting...")
-db = processData.process_database_file("databases/breast-cancer-wisconsin/wdbc.data")
-db.to_string()
+db = processData.process_database_file("databases/soybean/soybean-small.data")
+# db.to_string()
+processData.data_correction(db.get_data(), 36)
 print("Finished.")

### 2019-09-05 classifier.py
Added a file to test classifier, finished classifier

@@ -1,0 +1,31 @@
+
+def separateData(attributes, data, attToClassify):
+    """
+    [[1,2,3],[1,2,3]]
+    """
+    # attributes: ["Foo"..."Bar"]
+    # data: [[1,2,3],[1,2,3]]
+    # attToClassify: "Foo", A string matching the column name, or attribute, of the dataset
+    # Creating a dictionary to hold the class types
+    indexOfAttribute = attributes.index(attToClassify)
+    dataClasses = {}
+    for i in range(len(data)):
+        example = data[i]
+        if example[indexOfAttribute] not in dataClasses:
+            dataClasses[example[indexOfAttribute]] = []
+        dataClasses[example[indexOfAttribute]].append(example)
+    return dataClasses
+
+
+def attributeCount(subset): #TODO find a better name for this function
+    # acquire list of attributes
+    attributes = []
+    
+    for a in attributes:
+        getCount()
+
+def getCount(attribute, data):
+    return 1
+    
+          
+

### 2019-09-05 classifierTesting.py

@@ -1,0 +1,4 @@
+from classifier import separateData
+
+dataset = [[1,20,1], [2,21,0], [3,22,1]]
+print(separateData(["apples","bananas", "oranges"],dataset,"oranges"))

### 2019-09-05 classifier.py
Added function getCount and attributeCount

@@ -1,0 +1,34 @@
+import fileIO
+
+def classifyData(attributes, data, attToClassify):
+    """
+    [[1,2,3],[1,2,3]]
+    """
+    # attributes: []
+    # data: [[1,2,3],[1,2,3]]
+    # attToClassify: "Foo", A string matching the column name, or attribute, of the dataset
+    # Creating a dictionary to hold the class types
+    dataClasses = {}
+    for i in range(len(data))
+        example = data[i]
+        if example[i] not in dataClasses:
+            data[example[i]] = []
+        dataClasses.append(example)
+    return dataClasses
+
+
+def attributeCount(subset): #TODO find a better name for this function
+    # acquire list of attributes
+    attributes = []
+    
+    for a in attributes:
+        getCount()
+
+
+def getCount(attribute, data): #TODO find a better name for this one as well
+    for row in data:
+         
+    
+        
+    
+

### 2019-09-06 classifier.py
Made some progress on attributeCount function

@@ -1,4 +1,6 @@
 
+import numpy as np
+
 def separateData(attributes, data, attToClassify):
     """
     [[1,2,3],[1,2,3]]
@@ -18,11 +20,17 @@ def separateData(attributes, data, attToClassify):
 
 
 def attributeCount(subset): #TODO find a better name for this function
-    # acquire list of attributes
-    attributes = []
-    
-    for a in attributes:
-        getCount()
+    # get dimensions of subset
+    rows, cols = subset.shape
+    for col in subset.T:
+        for val in col:
+            # https://ask.sagemath.org/question/10279/frequency-count-in-numpy-array/
+            # got this count method from above link
+            count = list(col).count(val)
+            print(val, ': ', count) 
+        print('----------')
+    # for a in attributes:
+    #     getCount(a, subset)
 
 
 def getCount(attribute, data):

### 2019-09-06 classifierTesting.py

@@ -1,4 +1,20 @@
-from classifier import separateData
+from classifier import separateData, attributeCount
+import numpy as np
 
 dataset = [[1,20,1], [2,21,0], [3,22,1]]
-print(separateData(["apples","bananas", "oranges"],dataset,"oranges"))
+#print(separateData(["apples","bananas", "oranges"],dataset,"oranges"))
+
+subset = np.array([ #test subset I'm using
+    [1, 20, 1],
+    [3, 22, 1],
+    [5, 9, 1],
+    [2, 6, 1],
+    [1, 4, 1],
+    [5, 6, 1]
+])
+
+attributeCount(subset)
+
+
+
+

### 2019-09-06 Driver.py
Troy-Dana Cleaned up data files, Added frequency table

@@ -1,7 +1,0 @@
-import processData
-
-print("Starting...")
-db = processData.process_database_file("databases/soybean/soybean-small.data")
-# db.to_string()
-processData.data_correction(db.get_data(), 36)
-print("Finished.")

### 2019-09-06 classifier.py

@@ -1,31 +1,0 @@
-
-def separateData(attributes, data, attToClassify):
-    """
-    [[1,2,3],[1,2,3]]
-    """
-    # attributes: ["Foo"..."Bar"]
-    # data: [[1,2,3],[1,2,3]]
-    # attToClassify: "Foo", A string matching the column name, or attribute, of the dataset
-    # Creating a dictionary to hold the class types
-    indexOfAttribute = attributes.index(attToClassify)
-    dataClasses = {}
-    for i in range(len(data)):
-        example = data[i]
-        if example[indexOfAttribute] not in dataClasses:
-            dataClasses[example[indexOfAttribute]] = []
-        dataClasses[example[indexOfAttribute]].append(example)
-    return dataClasses
-
-
-def attributeCount(subset): #TODO find a better name for this function
-    # acquire list of attributes
-    attributes = []
-    
-    for a in attributes:
-        getCount()
-
-def getCount(attribute, data):
-    return 1
-    
-          
-

### 2019-09-06 processData.py

@@ -1,42 +1,0 @@
-from database import database as db
-
-# Loads the file contents into a database object
-def process_database_file(file_name):
-    file = open(file_name, "r")
-    # TODO: Change to use numpy for efficiency's sake?
-    data = []
-    for set in file:
-        # Converts the string line from the file into a set of values.
-        data.append(string_to_set(set))
-            
-    file.close()
-    database = db(data)
-
-    return database
-
-# Converts comma seperated strings into a set of values.
-def string_to_set(value):
-    value = value.strip('\n')
-    value_set = value.split(",")
-    return value_set
-
-# Either removes data with missing parameters, or extrapolates missing data using bootstraping methodology.
-def data_correction(database, parameter_count):
-    
-    correction_queue = []
-    
-    # Checks if the data from a specific row has all of the required parameters. If not, pops it from the list into a later processing queue.
-    for data in database:
-        if len(data) is not parameter_count:
-            correction_queue.append(data)
-            database.remove(data)
-            
-    print(correction_queue)
-
-# Deal with missing attributes
-    # Remove if 'low' number of missing attributes.
-    # Otherwise: Generate a random attribute from a pool of prexisting ones?
-        # Set up a queue of lines that need to do this, so we have the pool already fully generated.
-            # DOCUMENT THIS CHOICE.
-            
-# 

### 2019-09-06 src/classifier.py

@@ -1,0 +1,81 @@
+""" -------------------------------------------------------------
+@file        classifier.py
+@authors     George Engel, Troy Oster, Dana Parker, Henry Soule
+@brief       Contains methods used to classify attributes for data
+"""
+
+""" -------------------------------------------------------------
+@param  attributes          TODO: Is this a list of every attribute, or? Dana
+@param  data                TODO: What kind of data? Dana
+@param  attr_to_classify    The given attribute to classify
+
+@return     A hash table in the form of: { <class>: [<matching examples (rows)>] }
+            (described in @brief)
+@brief      This method creates a dictionary of the classes present for a given attribute
+            (form illustrated in @return)
+"""
+import collections
+def separate_data(attributes, data, attr_to_classify):
+    # attributes:     ["Foo"..."Bar"]
+    # data:           [[1,2,3],[1,2,3]]
+    # att_to_classify: "Foo", A string matching the column name, or attribute, of the dataset
+    # return { <Attribute to classify by>: { <ClassValue>:[<example or row>] } }
+    # Creating a dictionary to hold the class types
+    index_of_class = attributes.index(attr_to_classify)
+    data_classes = {attr_to_classify:{} }
+    for rowIndex in range(len(data)):
+        example = data[rowIndex]
+        if example[index_of_class] not in data_classes[attr_to_classify]:
+            data_classes[attr_to_classify][example[index_of_class]] = []
+        data_classes[attr_to_classify][example[index_of_class]].append(example)
+    return data_classes
+#Referenced/Copied https://stackoverflow.com/questions/39272862/is-printing-defaultdict-supposed-to-be-ugly-non-human-readable-by-default
+# User Martineau for how to be able to declare nested keys without using nested if statements
+# Didn't feel the need to reinvent the wheel, also it is only for data storage purposes
+class Tree(dict):
+    def __missing__(self, key):
+        value = self[key] = type(self)()
+        return value
+
+def genDataTable(attributes, data, attr_to_classify):
+    dataTable = Tree()
+    index_of_class = attributes.index(attr_to_classify)
+    for rowIndex in range(len(data)):
+        row = data[rowIndex]
+        for attributeIndex in range(len(row)) :
+                if attributeIndex != index_of_class:
+                    if row[attributeIndex] not in dataTable[row[index_of_class]][attributes[attributeIndex]]:
[…]

### 2019-09-06 src/database.py

@@ -1,0 +1,26 @@
+""" -------------------------------------------------------------
+@file        database.py
+@authors     George Engel, Troy Oster, Dana Parker, Henry Soule
+@brief       Object that stores the information of
+             each data repository
+
+TODO: Change the brief for data_array in case I'm wrong —Dana
+"""
+
+class database:
+    """
+    @param  data_array  List of pre-processed data from
+                        one data repository
+    
+    FIXME: Modify @param data_array's description 
+           in case I'm wrong —Dana
+    """
+    def __init__(self, data_array):
+        print("Database initialized.")
+        self.data = data_array
+        
+    def to_string(self):
+        print(self.data)
+        
+    def get_data(self):
+        return self.data

### 2019-09-06 src/main.py

@@ -1,0 +1,13 @@
+""" -------------------------------------------------------------
+@file        main.py
+@authors     George Engel, Troy Oster, Dana Parker, Henry Soule
+@brief       The file that runs the program
+"""
+
+import process_data
+
+print("Starting...")
+db = process_data.process_database_file("../databases/soybean/soybean-small.data")
+# db.to_string()
+process_data.data_correction(db.get_data(), 36)
+print("Finished.")

### 2019-09-06 src/process_data.py

@@ -1,0 +1,68 @@
+""" -------------------------------------------------------------
+@file        process_data.py
+@authors     George Engel, Troy Oster, Dana Parker, Henry Soule
+@brief       Imports and pre-processes data repositories
+"""
+
+from database import database as db
+
+""" -------------------------------------------------------------
+@param  input_database  The database file (of type .data) to be processed
+
+@return     The pre-processed data from input_db as a database object
+            (see database.py)
+@brief      Loads the file contents into a database object
+"""
+# FIXME: Change to use numpy for efficiency's sake?
+def process_database_file(input_db):
+
+    current_db_file = open(input_db, 'r')
+    db_data = []
+
+    for line in current_db_file:
+        # Converts the string line from the file into a set of values.
+        db_data.append(csv_to_set(line))
+            
+    current_db_file.close()
+
+    return db(db_data)
+
+""" -------------------------------------------------------------
+@param  input_csv   Comma-seperated string to convert
+
+@return     A set of values found in input_csv
+@brief      Converts comma seperated strings into a set of values
+"""
+def csv_to_set(input_csv):
+    return input_csv.strip('\n').split(',')
+
+""" -------------------------------------------------------------
+@param  database        Input database to operate upon per @brief
+@param  parameter_count FIXME: I don't know what this represents.
+                               What do you mean by a "parameter" here? —Dana
+
+@return     TODO (unless this doesn't return anything and I'm dumb) —Dana
+@brief      Either removes data with missing parameters,
+            or extrapolates missing data using bootstraping methodology.
+"""
+def data_correction(input_db, parameter_count):
+    
+    # TODO: Describe the local variable(s) below —Dana
+    correction_queue = []
+    
+    # Checks if the data from a specific row
+    # has all of the required parameters.
+    # If not, pops it from the list into a later processing queue.
+    for data in input_db:
+        if len(data) is not parameter_count:
+            correction_queue.append(data)
+            input_db.remove(data)
+            
+    print(correction_queue)
+
+# TODO: Implement the pseudocode below —Dana
+# Deal with missing attributes
+    # If 'low' number of missing attributes: remove.
+    # Else: Generate a random attribute from a pool of prexisting ones?
+        # Set up a queue of lines that need to do this, so we have the pool already fully generated.
+            # TODO: DOCUMENT THIS CHOICE.

### 2019-09-06 src/process_data.py
Minor format changes

@@ -38,29 +38,33 @@ def csv_to_set(input_csv):
 
 """ -------------------------------------------------------------
 @param  database        Input database to operate upon per @brief
-@param  parameter_count FIXME: I don't know what this represents.
-                               What do you mean by a "parameter" here? —Dana
+@param  attribute_count The amount of expected attributes for each row of data.
 
-@return     TODO (unless this doesn't return anything and I'm dumb) —Dana
+@return     input_db, correction_que : returns the 'clean' rows of data (input_db), and the rows of any malformed data (correction_queue).
+            PS: You aren't dumb Dana -George
 @brief      Either removes data with missing parameters,
             or extrapolates missing data using bootstraping methodology.
 """
-def data_correction(input_db, parameter_count):
+def data_correction(input_db, attribute_count):
     
-    # TODO: Describe the local variable(s) below —Dana
+    # Holds the rows of data that appear to be missing some attributes
     correction_queue = []
     
     # Checks if the data from a specific row
     # has all of the required parameters.
     # If not, pops it from the list into a later processing queue.
     for data in input_db:
-        if len(data) is not parameter_count:
+        if len(data) is not attribute_count:
             correction_queue.append(data)
             input_db.remove(data)
             
     print(correction_queue)
 
-# TODO: Implement the pseudocode below —Dana
+    return input_db, correction_queue
+
+# Deals with missing attributes of data by etiher removing them, if the number of 
+def extrapolate():
+    
 # Deal with missing attributes
     # If 'low' number of missing attributes: remove.
     # Else: Generate a random attribute from a pool of prexisting ones?

### 2019-09-06 src/database.py
Added appropriate descriptions to database.

@@ -1,19 +1,14 @@
 """ -------------------------------------------------------------
-@file        database.py
-@authors     George Engel, Troy Oster, Dana Parker, Henry Soule
-@brief       Object that stores the information of
-             each data repository
-
-TODO: Change the brief for data_array in case I'm wrong —Dana
+@file       database.py
+@authors    George Engel, Troy Oster, Dana Parker, Henry Soule
+@brief      Object that stores the information of
+            each data repository for ease of access & manipulation
 """
 
 class database:
     """
-    @param  data_array  List of pre-processed data from
-                        one data repository
-    
-    FIXME: Modify @param data_array's description 
-           in case I'm wrong —Dana
+    @param  data_array  List of data from one data repository
+                        that will be or has been filtered.
     """
     def __init__(self, data_array):
         print("Database initialized.")

### 2019-09-06 src/main.py
function output cleanup

@@ -9,5 +9,7 @@ import process_data
 print("Starting...")
 db = process_data.process_database_file("../databases/soybean/soybean-small.data")
 # db.to_string()
-process_data.data_correction(db.get_data(), 36)
+normal_data, irregular_data = process_data.data_correction(db.get_data(), 36)
+print("Normal Data:\n" + str(normal_data))
+print("Irregular Data:\n" + str(irregular_data))
 print("Finished.")

### 2019-09-06 src/process_data.py

@@ -58,15 +58,15 @@ def data_correction(input_db, attribute_count):
             correction_queue.append(data)
             input_db.remove(data)
             
-    print(correction_queue)
-
     return input_db, correction_queue
 
 # Deals with missing attributes of data by etiher removing them, if the number of 
 def extrapolate():
+    pass
     
 # Deal with missing attributes
     # If 'low' number of missing attributes: remove.
     # Else: Generate a random attribute from a pool of prexisting ones?
         # Set up a queue of lines that need to do this, so we have the pool already fully generated.
             # TODO: DOCUMENT THIS CHOICE.
+            

### 2019-09-06 src/main.py
Some printout clean up for the sake of my sanity.

@@ -3,13 +3,28 @@
 @authors     George Engel, Troy Oster, Dana Parker, Henry Soule
 @brief       The file that runs the program
 """
-
 import process_data
 
+# Cleaner print outs for the sake of my sanity.
+def print_database(database):
+    
+    if len(database) < 1:
+        print("[] - Empty")
+    else:
+        for row in database:
+            print(row)
+
 print("Starting...")
-db = process_data.process_database_file("../databases/soybean/soybean-small.data")
-# db.to_string()
-normal_data, irregular_data = process_data.data_correction(db.get_data(), 36)
-print("Normal Data:\n" + str(normal_data))
-print("Irregular Data:\n" + str(irregular_data))
-print("Finished.")
+# TODO: Enter user input for pathing. -George
+# TODO: Make pathing manager for choosing database -George
+db = process_data.process_database_file("../databases/breast-cancer-wisconsin/breast-cancer-wisconsin.data")
+
+normal_data, irregular_data = process_data.data_correction(db.get_data(), 11)
+
+print("\nNormal Data:")
+print_database(normal_data)
+
+print("\nIrregular Data:")
+print_database(irregular_data)
+
+print("\nFinished.")

### 2019-09-12 src/loss_functions.py
Add precision and recall functions

@@ -1,0 +1,23 @@
+import numpy as np
+
+def precision_binary(TP, FP):
+    return TP / (TP + FP)
+
+def recall_binary(TP, FN):
+    return TP / TP + FN
+
+def precision_non_binary(TP, FP):
+    precision = 0
+    for i in range(len(TP)):
+        precision += TP[i] / (TP[i] + FP[i])
+    return  (1 / len(TP)) * precision
+
+def recall_non_binary(TP, FN):
+    recall = 0
+    for i in range(len(TP)):
+        recall += TP[i] / (TP[i] + FN[i])
+    
+    return (1 / len(TP)) * recall
+
+
+

### 2019-09-12 src/main.py
Quantitative to categorical methods finished
-width based, cause I'm lazy.

@@ -85,7 +85,12 @@ db.set_data(repaired_db)
 
 db.shuffle_all(.1)
 
-print("Shuffled data:")
+print("\n\nShuffled data:\n\n")
+print_database(db.get_data())
+
+process_data.convert(db.get_data())
+
+print("\n\n\nFINAL DATABASE:\n\n\n")
 print_database(db.get_data())
 # # -------------------------------------------------------------
 

### 2019-09-12 src/classifier.py
Edited my calculate_class function

@@ -134,8 +134,19 @@ def classify_db(attrs, db, class_idx):
 def calculate_class(example, training_data_tbl, class_idx):
     print("Example: ", example)
     C = [] # Array to store probabilities of each class
+    Q = [] 
+    total_data = 0
+    # For each class in the training data
+    for c in training_data_tbl:
+        count = training_data_tbl[c]['count']
+        total_data += count
+        Q.append(count)
+    
+    Q = [x / total_data for x in Q]
+    
     # Iterate over each class in training data table
     for classifier in training_data_tbl:
+        print(training_data_tbl[classifier])
         prob = 1
         idx = 0
         # Iterate through values for each classifier

### 2019-09-12 src/classifier_testing.py

@@ -13,10 +13,10 @@ from path_manager import pathManager as pm
 full_path = "/Users/admin/Desktop/2019 Fall Semester/Machine Learning/CSCI-447-Project-1/databases/iris/iris.data"
 db = process_data.process_database_file(full_path)
 
-normal_data, irregular_data = process_data.identify_missing_data(db.get_data())
+normal_data, irregular_data = process_data.identify_missing_data(db.get_data(), 'sepal width in cm')
 normal_data = normal_data[0:len(normal_data)-1] # last row is empty so the code wasn't running
 
-attrs = ["sepal length", "sepal width", "petal length", "petal width", "class"] 
+attrs = ["sepal length", "sepal width", "petal length", "petal width", "class"]
 # classified_data = separate_data(attrs, normal_data, "class")['class']
 classified_data = classifier.classify_db(attrs, normal_data, 4)
 classified_data = classifier.calc_prob_of_response(classified_data)

### 2019-09-12 src/loss_functions.py

@@ -1,4 +1,8 @@
 import numpy as np
+from classifier import classify_db, calculate_class, calc_prob_of_response
+import os
+import process_data
+from path_manager import pathManager as pm
 
 def precision_binary(TP, FP):
     return TP / (TP + FP)
@@ -8,16 +12,34 @@ def recall_binary(TP, FN):
 
 def precision_non_binary(TP, FP):
     precision = 0
+    
     for i in range(len(TP)):
         precision += TP[i] / (TP[i] + FP[i])
+    
     return  (1 / len(TP)) * precision
 
+# FP = [2,3,4]
+# TN = [1,6,7]
 def recall_non_binary(TP, FN):
     recall = 0
+    
     for i in range(len(TP)):
         recall += TP[i] / (TP[i] + FN[i])
     
     return (1 / len(TP)) * recall
 
+path_manager = pm()
+path_manager.set_current_selected_folder('iris')
+db = process_data.process_database_file(path_manager)
+normal_data, irregular_data = process_data.identify_missing_data(db.get_data(), 'sepal width in cm')
+
+
+attrs = ["sepal length", "sepal width", "petal length", "petal width", "class"]
+
+classified_data = classify_db(attrs, normal_data, 4)
+training_data = calc_prob_of_response(classified_data)
+print(training_data)
+
+# calculate_class(normal_data[0], training_data, 4)
 
 

### 2019-09-12 src/classifier.py
Updated calculate_class function, added class_probs function.

@@ -125,42 +125,54 @@ def classify_db(attrs, db, class_idx):
 
 #     return prob_table
 
-
-# -------------------------------------------------------------
-# Guess the class of an example
-# @param example a row from the test set that we are trying to classify
-# @param training_data_tbl the training data
-# @param class_idx the index of the column that stores the class for each row in the data
-def calculate_class(example, training_data_tbl, class_idx):
-    print("Example: ", example)
-    C = [] # Array to store probabilities of each class
-    Q = [] 
-    total_data = 0
+'''--------------------------------------------------------------
+Calculate proportions/probabilities of each class within the data set
+@param data - The data Tree, with the class counts included
+@return a set containing the probabilities for each class
+'''
+def get_class_probs(data):
+    Q = [] # Set to store class probs
+    total_data = 0 # Will store the total size of the data set
     # For each class in the training data
-    for c in training_data_tbl:
-        count = training_data_tbl[c]['count']
+    for c in data:
+        count = data[c]['count']
         total_data += count
         Q.append(count)
     
     Q = [x / total_data for x in Q]
-    
+    return Q
+
+''' -------------------------------------------------------------
+Guess the class of an example
+@param  example a row from the test set that we are trying to classify
+@param  tbd     the training data table
+@param  class_idx   the index of the column that stores the class for each row in the data
+@return the predicted class
+'''
+import numpy as np
+def calculate_class(example, tbd, class_probs, class_idx):
+    # print("Example: ", example)
+    C = [] # Array to store probabilities of each class
+
     # Iterate over each class in training data table
-    for classifier in training_data_tbl:
-        print(training_data_tbl[classifier])
+    for classifier in tbd:
+        # print(tbd[classifier])
         prob = 1
         idx = 0
         # Iterate through values for each classifier
-        for attr in training_data_tbl[classifier]:
+        for attr in tbd[classifier]:
             if attr != 'count':
                 if idx != class_idx:
-                    if training_data_tbl[classifier][attr][example[idx]][1] != {}:
-                        prob *= training_data_tbl[classifier][attr][example[idx]][1]
+                    if tbd[classifier][attr][example[idx]][1] != {}:
+                        prob *= tbd[classifier][attr][example[idx]][1]
                     else:
                         prob *= 0
                 idx = idx + 1
         C.append(prob)
 
-    print(C)
+    C = [class_probs[i] * C[i] for i in range(len(C))]
+    return np.argmax(C)
+    
 
[…]

### 2019-09-12 src/loss_functions.py

@@ -1,5 +1,6 @@
 import numpy as np
-from classifier import classify_db, calculate_class, calc_prob_of_response
+# from classifier import classify_db, calculate_class, calc_prob_of_response, separate_data
+from classifier import *
 import os
 import process_data
 from path_manager import pathManager as pm
@@ -10,6 +11,13 @@ def precision_binary(TP, FP):
 def recall_binary(TP, FN):
     return TP / TP + FN
 
+'''----------------------------------------
+Calculate precision for data with non-binary classification
+@param TP - set of true positive counts, i.e. the number, for each class, of
+examples that were correctly classifified. TP[i] = number of examples correctly 
+classified as class i
+@param FP - set of false positive counts
+'''
 def precision_non_binary(TP, FP):
     precision = 0
     
@@ -37,9 +45,15 @@ normal_data, irregular_data = process_data.identify_missing_data(db.get_data(), 
 attrs = ["sepal length", "sepal width", "petal length", "petal width", "class"]
 
 classified_data = classify_db(attrs, normal_data, 4)
-training_data = calc_prob_of_response(classified_data)
-print(training_data)
+class_probs = get_class_probs(classified_data)
+classified_data = calc_prob_of_response(classified_data)
 
-# calculate_class(normal_data[0], training_data, 4)
+binified_data = separate_data(attrs, db.get_data(), 'class')
+
+for row in binified_data:
+    if row[0] == 0:
+        # Let's start guessing!
+        print("ACTUAL ROW:")
+
 
 

### 2019-09-12 src/k_fold_cross_validation.py
Almost done with k-fold cross validation

@@ -1,0 +1,44 @@
+import classifier
+from copy import deepcopy
+
+def k_fold(k,binned_data_set,bin_lengths):
+    #print (binned_data_set)
+    incorrect_guesses = []
+    correct_guesses = []
+    temp_attr_headers = ['pol','a2','a3','a4','a5','a6','a7','a8','a9','a10','a11','a12','a13','a14','a15','a16','a17']
+    #classified_data = classifier.classify_db(temp_attr_headers, repaired_db, 0)
+    for bin_number in range(k):
+        test_data = []
+        print("\n \n BINNED DATA SET")
+        print(binned_data_set)
+        training_data = deepcopy(binned_data_set)
+        row_idx = 0
+        print(" \n \nTraining Data Set \n \n")
+        print(training_data)
+        while len(test_data) < bin_lengths[bin_number]:
+            #print("len Test_Data " + str(len(test_data)))
+            #print("bin length " + str(bin_lengths[bin_number]))
+            #print("row" + str(row_idx))
+            if training_data[row_idx][0] == bin_number:
+                test_data.append(training_data.pop(row_idx).copy()[1:])
+                row_idx -=1
+            row_idx += 1
+
+        for row_idx2 in range(len(training_data)):
+            training_data[row_idx2].pop(0)
+
+        
+        classified_training_data = classifier.classify_db(temp_attr_headers, training_data, 0)
+        training_probs = classifier.calc_prob_of_response(classified_training_data)
+        for test_row in test_data:
+            predicted = classifier.predict(training_probs, ['a2','a6'], temp_attr_headers, test_row)
+            if  predicted== test_row[0]:
+                correct_guesses.append([predicted])
+            else:
+                incorrect_guesses.append([test_row[0],predicted])
+
+        print('\n \n \n Correct Guesses: \n \n')
+        print(len(correct_guesses))
+        print('\n \n \n Incorrect Guesses: \n \n')
+        print(len(incorrect_guesses))
+        print(" \n \n \n training probs \n \n \n" + str(training_probs))

### 2019-09-12 src/main.py

@@ -6,6 +6,7 @@
 import os
 import process_data
 import classifier
+import k_fold_cross_validation
 from path_manager import pathManager as pm
 
 # Asks for user to select a database from a list presented from current database collection directory.
@@ -74,8 +75,8 @@ corrected_data = process_data.extrapolate_data(normal_data, irregular_data)
 
 # -------------------------------------------------------------
 
-print("\n\n\n\n\nCorrected Irregular Data:")
-print_database(corrected_data)
+#print("\n\n\n\n\nCorrected Irregular Data:")
+#print_database(corrected_data)
 #print("Irregular data total:", len(irregular_data))
 #print("Regular data total:", len(normal_data))
 #rint("Corrected data total:", len(corrected_data))
@@ -90,22 +91,25 @@ db.set_data(repaired_db)
 
 db.shuffle_data(.1, 2)
 
-print("Shuffled data:")
-print_database(db.get_data())
+#print("Shuffled data:")
+#print_database(db.get_data())
 # -------------------------------------------------------------
 
-print("\nRunning classifier...")
-print('\n\n\n\n\nRunning classify_db():')
+#print("\nRunning classifier...")
+#print('\n\n\n\n\nRunning classify_db():')
 
 temp_attr_headers = ['pol','a2','a3','a4','a5','a6','a7','a8','a9','a10','a11','a12','a13','a14','a15','a16','a17']
 classified_data = classifier.classify_db(temp_attr_headers, repaired_db, 0)
 
-print(classified_data)
+#print(classified_data)
 
-print("\n\nRunning calc_prob_of_response():")
+#print("\n\nRunning calc_prob_of_response():")
 probs = classifier.calc_prob_of_response(classified_data)
-print('\n\nprobs:\n')
-print(probs)
-print('\n\nprobs Products:\n')
-print(classifier.predict(probs,['a2'],temp_attr_headers,repaired_db[0]))
+#print('\n\nprobs:\n')
+#print(probs)
+#print('\n\nprobs Products:\n')
+#print(classifier.predict(probs,['a2'],temp_attr_headers,repaired_db[0]))
+#print('\n\nBinified Data:\n')
+#print(classifier.separate_data(temp_attr_headers,db.get_data())[0])
+k_fold_cross_validation.k_fold(10,classifier.separate_data(temp_attr_headers,db.get_data())[0],classifier.separate_data(temp_attr_headers,db.get_data())[1])
 print("\nFinished.")

### 2019-09-12 src/k_fold_cross_validation.py
kfold updated to support bin based prediction results

@@ -3,11 +3,17 @@ from copy import deepcopy
 
 def k_fold(k,binned_data_set,bin_lengths):
     #print (binned_data_set)
-    incorrect_guesses = []
-    correct_guesses = []
+    binned_guess_results = []
     temp_attr_headers = ['pol','a2','a3','a4','a5','a6','a7','a8','a9','a10','a11','a12','a13','a14','a15','a16','a17']
     #classified_data = classifier.classify_db(temp_attr_headers, repaired_db, 0)
+    '''
+        binned_guess_results: [[<incorrect_guesses>, <correct_guesses>]]
+        incorrect_guesses: [[expected answer,incorrect guess]]
+        correct_guesses: [correct guess]
+    '''
     for bin_number in range(k):
+        incorrect_guesses = []
+        correct_guesses = []
         test_data = []
         print("\n \n BINNED DATA SET")
         print(binned_data_set)
@@ -33,12 +39,14 @@ def k_fold(k,binned_data_set,bin_lengths):
         for test_row in test_data:
             predicted = classifier.predict(training_probs, ['a2','a6'], temp_attr_headers, test_row)
             if  predicted== test_row[0]:
-                correct_guesses.append([predicted])
+                correct_guesses.append(predicted)
             else:
                 incorrect_guesses.append([test_row[0],predicted])
-
+        binned_guess_results.append([incorrect_guesses,correct_guesses])
         print('\n \n \n Correct Guesses: \n \n')
         print(len(correct_guesses))
         print('\n \n \n Incorrect Guesses: \n \n')
         print(len(incorrect_guesses))
         print(" \n \n \n training probs \n \n \n" + str(training_probs))
+
+    print(binned_guess_results)

### 2019-09-12 src/main.py

@@ -97,9 +97,9 @@ print_database(db.get_data())
 
 # print("\nRunning classifier...")
 # print('\n\n\n\n\nRunning classify_db():')
-
+temp_attr_headers = ['pol','a2','a3','a4','a5','a6','a7','a8','a9','a10','a11','a12','a13','a14','a15','a16','a17']
 k_fold_cross_validation.k_fold(10,classifier.separate_data(temp_attr_headers,db.get_data())[0],classifier.separate_data(temp_attr_headers,db.get_data())[1])
-# temp_attr_headers = ['pol','a2','a3','a4','a5','a6','a7','a8','a9','a10','a11','a12','a13','a14','a15','a16','a17']
+
 # classified_data = classifier.classify_db(temp_attr_headers, repaired_db, 0)
 
 # print(classified_data)

### 2019-09-12 src/classifier.py
Removed some debug print statements.

@@ -156,9 +156,11 @@ def calculate_class(example, tbd, class_probs, class_idx):
 
     # Iterate over each class in training data table
     for classifier in tbd:
-        # print(tbd[classifier])
         prob = 1
-        idx = 0
+        # idx stores the index of the current attribute of the example
+        # we are evaluating. set to 1, b/c first number in each example 
+        # is the bin number.
+        idx = 1
         # Iterate through values for each classifier
         for attr in tbd[classifier]:
             if attr != 'count':

### 2019-09-12 src/loss_functions.py

@@ -49,11 +49,15 @@ class_probs = get_class_probs(classified_data)
 classified_data = calc_prob_of_response(classified_data)
 
 binified_data = separate_data(attrs, db.get_data(), 'class')
+classes = ['Iris-setosa', 'Iris-versicolor', 'Iris-verginica']
 
 for row in binified_data:
-    if row[0] == 0:
+    if row[0] == 9:
         # Let's start guessing!
-        print("ACTUAL ROW:")
+        print("ROW: ", row)
+        idx = calculate_class(row, classified_data, class_probs, 5)
+        print("GUESSED CLASS: ", classes[idx])
+        print("------------------------------")
 
 
 

### 2019-09-12 src/process_data.py
Auto stash before merge of "master" and "origin/master"

@@ -38,10 +38,10 @@ def process_database_file(path_manager):
         
 
     
-    attributes = read_attributes(path_manager.get_current_selected_dir(), data_filename)
+    attributes, classifier_column, classifier_attr_cols = read_attributes(path_manager.get_current_selected_dir(), data_filename)
 
     print(attributes)
-    return db(db_data, attributes)
+    return db(db_data, attributes, classifier_column, classifier_attr_cols)
 
 # Reads in the attribute file from a database, and returns the attributes as a list
 def read_attributes(directory, data_filename):
@@ -51,15 +51,18 @@ def read_attributes(directory, data_filename):
     
     attribute_file = open(full_path, 'r')
     
-    attributes = []
-    for attribute in attribute_file:
-        value = attribute.strip('\n')
-        if value is not "":
-            attributes.append(value)
-        
-    return attributes
-        
-        
+    # Reads in attributes from line 1 and split/cleans into list
+    attributes = attribute_file.readline().strip('\n').split()
+    
+    # Reads in the index of the Classifier column.
+    classifier_column = int(attribute_file.readline().strip('\n'))
+    
+    # Reads in the indexes of the attributes used for classification
+    classifier_attr_cols = []
+    for cols in  attribute_file.readline().strip('\n').split():
+        classifier_attr_cols.append(int(cols))
+    
+    return attributes, classifier_column, classifier_attr_cols
     
 """ -------------------------------------------------------------
 @param  input_csv   Comma-seperated string to convert

### 2019-09-12 src/process_data.py
Added classifier column & parameter support

@@ -52,14 +52,14 @@ def read_attributes(directory, data_filename):
     attribute_file = open(full_path, 'r')
     
     # Reads in attributes from line 1 and split/cleans into list
-    attributes = attribute_file.readline().strip('\n').split()
+    attributes = attribute_file.readline().strip('\n').split(',')
     
     # Reads in the index of the Classifier column.
     classifier_column = int(attribute_file.readline().strip('\n'))
     
     # Reads in the indexes of the attributes used for classification
     classifier_attr_cols = []
-    for cols in  attribute_file.readline().strip('\n').split():
+    for cols in  attribute_file.readline().strip('\n').split(','):
         classifier_attr_cols.append(int(cols))
     
     return attributes, classifier_column, classifier_attr_cols

### 2019-09-12 src/loss_functions.py
Added a line of code

@@ -1,6 +1,6 @@
 import numpy as np
-# from classifier import classify_db, calculate_class, calc_prob_of_response, separate_data
 from classifier import *
+from k_fold_cross_validation import *
 import os
 import process_data
 from path_manager import pathManager as pm
@@ -48,16 +48,20 @@ classified_data = classify_db(attrs, normal_data, 4)
 class_probs = get_class_probs(classified_data)
 classified_data = calc_prob_of_response(classified_data)
 
-binified_data = separate_data(attrs, db.get_data(), 'class')
+# binified_data = separate_data(attrs, db.get_data(), 'class')
 classes = ['Iris-setosa', 'Iris-versicolor', 'Iris-verginica']
 
-for row in binified_data:
-    if row[0] == 9:
-        # Let's start guessing!
-        print("ROW: ", row)
-        idx = calculate_class(row, classified_data, class_probs, 5)
-        print("GUESSED CLASS: ", classes[idx])
-        print("------------------------------")
+
+k_fold(10, classifier.separate_data(attrs,db.get_data())[0],classifier.separate_data(attrs,db.get_data())[1])
+
+
+# for row in binified_data:
+#     if row[0] == 9:
+#         # Let's start guessing!
+#         print("ROW: ", row)
+#         idx = calculate_class(row, classified_data, class_probs, 5)
+#         print("GUESSED CLASS: ", classes[idx])
+#         print("------------------------------")
 
 
 

### 2019-09-12 src/database.py
Added support for missing symbol in attr file

@@ -12,12 +12,13 @@ class database:
     @param  data_array  List of data from one data repository
                         that will be or has been filtered.
     """
-    def __init__(self, data_array, attrs, classifier_col, classifier_attr_cols):
+    def __init__(self, data_array, attrs, classifier_col, classifier_attr_cols, symbol):
         print("Database initialized.")
         self.data = data_array
         self.attributes = attrs
         self.classifier_column = classifier_col
         self.classifier_attr_columns = classifier_attr_cols
+        self.missing_symbol = symbol
         
     def to_string(self):
         print(self.data)
@@ -36,6 +37,9 @@ class database:
     
     def get_classifier_attr_cols(self):
         return self.classifier_attr_columns
+    
+    def get_missing_symbol(self):
+        return self.missing_symbol
     
     def get_classifier_attribute_index(self):
         index = 0

### 2019-09-12 src/process_data.py

@@ -38,10 +38,10 @@ def process_database_file(path_manager):
         
 
     
-    attributes, classifier_column, classifier_attr_cols = read_attributes(path_manager.get_current_selected_dir(), data_filename)
+    attributes, classifier_column, classifier_attr_cols, missing_symbol = read_attributes(path_manager.get_current_selected_dir(), data_filename)
 
     print(attributes)
-    return db(db_data, attributes, classifier_column, classifier_attr_cols)
+    return db(db_data, attributes, classifier_column, classifier_attr_cols, missing_symbol)
 
 # Reads in the attribute file from a database, and returns the attributes as a list
 def read_attributes(directory, data_filename):
@@ -61,8 +61,10 @@ def read_attributes(directory, data_filename):
     classifier_attr_cols = []
     for cols in  attribute_file.readline().strip('\n').split(','):
         classifier_attr_cols.append(int(cols))
+        
+    missing_symbol = attribute_file.readline().strip('\n')
     
-    return attributes, classifier_column, classifier_attr_cols
+    return attributes, classifier_column, classifier_attr_cols, missing_symbol
     
 """ -------------------------------------------------------------
 @param  input_csv   Comma-seperated string to convert
@@ -162,7 +164,7 @@ def data_correction(input_db, attribute_count):
     # Checks if the data from a specific row
     # has all of the required parameters.
     # If not, pops it from the list into a later processing queue.
-    for data in input_db:
+    for data in input_db.get_data():
         if len(data) is not attribute_count:
             correction_queue.append(data)
             input_db.remove(data)
@@ -170,15 +172,15 @@ def data_correction(input_db, attribute_count):
     return input_db, correction_queue
 
 # Finds any ambiguous/missing data and returns the rows of the relevant database in which missing parameters occur.
-def identify_missing_data(input_db, missing_data_val):
+def identify_missing_data(input_db):
     
     # Holds the rows of data that appear to be missing some attributes
     correction_queue = []
     normal = []
-    for data in input_db:
+    for data in input_db.get_data():
         
         # Check for a missing parameter character:
-        if missing_data_val in data:
+        if input_db.get_missing_symbol() in data:
             # Adds data to que for correction
             correction_queue.append(data)
         else:

### 2019-09-12 src/main.py
Commented k_fold_cross_validation

@@ -98,7 +98,8 @@ print_database(db.get_data())
 # print("\nRunning classifier...")
 # print('\n\n\n\n\nRunning classify_db():')
 temp_attr_headers = ['pol','a2','a3','a4','a5','a6','a7','a8','a9','a10','a11','a12','a13','a14','a15','a16','a17']
-k_fold_cross_validation.k_fold(10,classifier.separate_data(temp_attr_headers,db.get_data())[0],classifier.separate_data(temp_attr_headers,db.get_data())[1])
+binned_data = classifier.separate_data(temp_attr_headers,db.get_data())
+k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1])
 
 # classified_data = classifier.classify_db(temp_attr_headers, repaired_db, 0)
 

### 2019-09-13 src/loss_functions.py
Implemented precision and recall functions

@@ -11,14 +11,66 @@ def precision_binary(TP, FP):
 def recall_binary(TP, FN):
     return TP / TP + FN
 
-'''----------------------------------------
-Calculate precision for data with non-binary classification
-@param TP - set of true positive counts, i.e. the number, for each class, of
-examples that were correctly classifified. TP[i] = number of examples correctly 
-classified as class i
-@param FP - set of false positive counts
 '''
-def precision_non_binary(TP, FP):
+binned_guess_results: [[<incorrect_guesses>, <correct_guesses>]]
+incorrect_guesses: [[expected answer,incorrect guess]]
+correct_guesses: [correct guess]
+'''
+guess_results = [
+    #bin 1:
+    [
+        #incorrect guesses:
+        [['republican', 'democrat'], ['democrat', 'republican'], ['democrat', 'republican']],
+        #correct guesses:
+        ['republican', 'democrat', 'democrat', 'republican']
+    ]
+]
+#bin:
+bin_results = [
+    [['republican', 'democrat'], ['democrat', 'republican'], ['democrat', 'republican']],
+    ['republican', 'democrat', 'democrat', 'republican', 'republican']
+]
+
+classes = ['republican', 'democrat']
+# Get true positive guesses
+def true_positives(bin_results, classes):
+    correct = bin_results[1]
+    TP = [0 for i in range(len(classes))]
+    for guess in correct:
+        TP[classes.index(guess)] += 1
+    return TP
+
+# Get false positive guesses
+def false_positives(bin_results, classes):
+    incorrect_guesses = bin_results[0]
+    FP = [0 for i in range(len(classes))]
+    for guess in incorrect_guesses:
+        FP[classes.index(guess[1])] += 1
+    return FP
+
+
+# Get false negative guesses
+def false_negatives(bin_results, classes):
+    incorrect_guesses = bin_results[0]
+    FN = [0 for i in range(len(classes))]
+    for guess in incorrect_guesses:
+        FN[classes.index(guess[0])] += 1
+    return FN
+
+print("True Positives: ", true_positives(bin_results, classes))
+print("False Positives: ", false_positives(bin_results, classes))
+print("False Negatives: ", false_negatives(bin_results, classes))
+
+
+'''----------------------------------------
+@param  bin_results the set of guesses for the current bin
+@param  classes     a set of the class names for the current dataset
+@return the precision score for this current bin
[…]

### 2019-09-13 src/loss_functions.py
Removed old code from loss_functions.py

@@ -5,31 +5,11 @@ import os
 import process_data
 from path_manager import pathManager as pm
 
-def precision_binary(TP, FP):
-    return TP / (TP + FP)
-
-def recall_binary(TP, FN):
-    return TP / TP + FN
-
-'''
-binned_guess_results: [[<incorrect_guesses>, <correct_guesses>]]
-incorrect_guesses: [[expected answer,incorrect guess]]
-correct_guesses: [correct guess]
-'''
-guess_results = [
-    #bin 1:
-    [
-        #incorrect guesses:
-        [['republican', 'democrat'], ['democrat', 'republican'], ['democrat', 'republican']],
-        #correct guesses:
-        ['republican', 'democrat', 'democrat', 'republican']
-    ]
-]
 #bin:
-bin_results = [
-    [['republican', 'democrat'], ['democrat', 'republican'], ['democrat', 'republican']],
-    ['republican', 'democrat', 'democrat', 'republican', 'republican']
-]
+# bin_results = [
+#     [['', ''], ['', 'republican'], ['democrat', 'republican']],
+#     ['republican', 'democrat', 'democrat', 'republican', 'republican']
+# ]
 
 classes = ['republican', 'democrat']
 # Get true positive guesses
@@ -57,10 +37,6 @@ def false_negatives(bin_results, classes):
         FN[classes.index(guess[0])] += 1
     return FN
 
-print("True Positives: ", true_positives(bin_results, classes))
-print("False Positives: ", false_positives(bin_results, classes))
-print("False Negatives: ", false_negatives(bin_results, classes))
-
 
 '''----------------------------------------
 @param  bin_results the set of guesses for the current bin
@@ -83,7 +59,9 @@ def precision_non_binary(bin_results, classes):
 @param  classes     a set of the class names for the current dataset
 @return the recall score for this current bin
 '''
-def recall_non_binary(TP, FN):
+def recall_non_binary(bin_results, classes):
+    TP = true_positives(bin_results, classes)
+    FN = false_negatives(bin_results, classes)
     recall = 0
     
     for i in range(len(TP)):

### 2019-09-13 src/classifier.py
Update calc_prob_of_repsonse() to not remove the 'count' key

@@ -84,14 +84,6 @@ def classify_db(attrs, db, class_idx):
     # Return the completed data structure per the form in @return
     return data_tbl
 
-# -----------
-# def calc_prob_of_response(raw_data, classified_data):
-
-#     ratios = {}
-
-#     for data_class in classified_data:
-#         print(data_class)
-
 # """ -------------------------------------------------------------
 # Calculate probabilities for each attribute value
 # This is step 2 in the algorithm
@@ -157,27 +149,44 @@ def calculate_class(example, training_data_tbl, class_idx):
             occuring in each class
 @brief      Converts each attribute value/response count into a probability
             of that value occuring within its class.
+            
             IMPORTANT: This is step 3 of "the algorithm"
 """
 def calc_prob_of_response(db):
 
+    # The total number of examples in a database
+    sample_size = 0
+
     # For each class in the database...
     for db_class in db:
+        for key, attr in list(db[db_class].items()):
 
-        # Acquire the total number of classes
-        # and remove that value from the local db variable
-        class_count = db[db_class].pop('count')
-        
-        # For each attribute within the class...
-        # "Divide the number of examples that match that attribute value (plus one)..."
-        # "...by the number of examples in the class (plus d) (d being number of attributes)"
-        for attr in db[db_class]:
+            # This formula doesn't apply to the count probability
+            if key != 'count':
 
-            for key in db[db_class][attr].keys():
-                db[db_class][attr][key][1] = \
-                (db[db_class][attr][key][0] + 1) / \
-                (class_count + len(db_class))
+                # For each attribute within the class...
+                # "Divide the number of examples that match that attribute value (plus one)..."
+                # "...by the number of examples in the class (plus d) (d being number of attributes)"
+                for val in attr:
+                    db[db_class][key][val][1] = \
+                    (db[db_class][key][val][0] + 1) / \
+                    (db[db_class]['count'] + len(db_class))
 
+            # If we are looking at the count attribute,
+            # add it to a generic total
+            elif key == 'count':
+                sample_size += db[db_class][key]
+    
+    # We need to re-loop through each class to get
+    # each classes probability
+    for db_class in db:
+
+        # Probability of a class is it's count divided by the sample size
+        temp = []
+        temp.append(db[db_class]['count'] )
+        temp.append(temp[0] / sample_size)
+        db[db_class]['count'] = temp
+    
     return db
 
[…]

### 2019-09-13 src/loss_functions.py
Cleaned up code a little

@@ -5,13 +5,6 @@ import os
 import process_data
 from path_manager import pathManager as pm
 
-#bin:
-# bin_results = [
-#     [['', ''], ['', 'republican'], ['democrat', 'republican']],
-#     ['republican', 'democrat', 'democrat', 'republican', 'republican']
-# ]
-
-classes = ['republican', 'democrat']
 # Get true positive guesses
 def true_positives(bin_results, classes):
     correct = bin_results[1]
@@ -69,32 +62,21 @@ def recall_non_binary(bin_results, classes):
     
     return (1 / len(TP)) * recall
 
-# path_manager = pm()
-# path_manager.set_current_selected_folder('iris')
-# db = process_data.process_database_file(path_manager)
-# normal_data, irregular_data = process_data.identify_missing_data(db.get_data(), 'sepal width in cm')
 
+#bin:
+bin_results = [
+    [
+        ['republican', 'democrat'], 
+        ['democrat', 'republican'], 
+        ['democrat', 'republican']
+    ],
+    ['republican', 'democrat', 'democrat', 'republican', 'republican']
+]
 
-# attrs = ["sepal length", "sepal width", "petal length", "petal width", "class"]
+classes = ['republican', 'democrat']
 
-# classified_data = classify_db(attrs, normal_data, 4)
-# class_probs = get_class_probs(classified_data)
-# classified_data = calc_prob_of_response(classified_data)
-
-# binified_data = separate_data(attrs, db.get_data(), 'class')
-# classes = ['Iris-setosa', 'Iris-versicolor', 'Iris-verginica']
-
-
-# k_fold(10, classifier.separate_data(attrs,db.get_data())[0],classifier.separate_data(attrs,db.get_data())[1])
-
-
-# for row in binified_data:
-#     if row[0] == 9:
-#         # Let's start guessing!
-#         print("ROW: ", row)
-#         idx = calculate_class(row, classified_data, class_probs, 5)
-#         print("GUESSED CLASS: ", classes[idx])
-#         print("------------------------------")
+print(precision_non_binary(bin_results, classes))
+print(recall_non_binary(bin_results, classes))
 
 
 

### 2019-09-13 src/k_fold_cross_validation.py
Small changes

@@ -1,5 +1,6 @@
 import classifier
 from copy import deepcopy
+from loss_functions import *
 
 """ -------------------------------------------------------------
 @param  k                   The number of folds we are using for k-fold cross validation
@@ -59,5 +60,8 @@ def k_fold(k,binned_data_set,bin_lengths):
         print('\n \n \n Incorrect Guesses: \n \n')
         print(len(incorrect_guesses))
         print(" \n \n \n training probs \n \n \n" + str(training_probs))
+        # precision_non_binary()
+        # recall_non_binary()
+
 
     print(binned_guess_results)

### 2019-09-13 src/loss_functions.py

@@ -75,8 +75,8 @@ bin_results = [
 
 classes = ['republican', 'democrat']
 
-print(precision_non_binary(bin_results, classes))
-print(recall_non_binary(bin_results, classes))
+# print(precision_non_binary(bin_results, classes))
+# print(recall_non_binary(bin_results, classes))
 
 
 

### 2019-09-13 src/classifier.py
Removed hard coded values in k-fold file

@@ -180,19 +180,17 @@ def calc_prob_of_response(db):
 
     return db
 
-def predict(probs, attr_for_prediction, attrs, data_to_predict):
+def predict(probs, attrs, data_to_predict, db):
+    attribute_indexes = db.get_classifier_attr_cols()
     probs_products = []
     classes = []
-    attribute_indexes = []
     for key in probs.keys():
         probs_products.append(1)
-    for attribute in attr_for_prediction:
-        attribute_indexes.append(attrs.index(attribute))
 
     for class_idx, data_class in enumerate(probs):
         classes.append(data_class)
         for attribute_idx in attribute_indexes:
-            if attribute_idx != 0:
+            if attribute_idx != db.get_classifier_col():
                 probs_products[class_idx] *= probs[data_class][attrs[attribute_idx]][data_to_predict[attribute_idx]][1]
     return classes[probs_products.index(max(probs_products))]
 

### 2019-09-13 src/k_fold_cross_validation.py

@@ -13,11 +13,10 @@ from copy import deepcopy
            Then classify the training data and calculate the probabilities. Run prediction on each row of the test_data set and return an array of guess results containing guess results
            associated with each bin, as every bin will be the test bin at some point.
 """
-def k_fold(k,binned_data_set,bin_lengths):
+def k_fold(k,binned_data_set,bin_lengths, db):
     #print (binned_data_set)
     binned_guess_results = []
-    temp_attr_headers = ['pol','a2','a3','a4','a5','a6','a7','a8','a9','a10','a11','a12','a13','a14','a15','a16','a17']
-    
+    attr_headers = db.get_attr()
     # For each bin in our data
     for bin_number in range(k):
         incorrect_guesses = []
@@ -37,14 +36,14 @@ def k_fold(k,binned_data_set,bin_lengths):
             training_data[row_idx2].pop(0)
 
         # Classify our training data set, so we can calculate the probabilites
-        classified_training_data = classifier.classify_db(temp_attr_headers, training_data, 0)
+        classified_training_data = classifier.classify_db(attr_headers, training_data, 0)
 
         # Calculate the probabilities
         training_probs = classifier.calc_prob_of_response(classified_training_data)
 
         # For each row (sample) in our test_data, try to predict its class
         for test_row in test_data:
-            predicted = classifier.predict(training_probs, ['a2','a6'], temp_attr_headers, test_row)
+            predicted = classifier.predict(training_probs, attr_headers, test_row, db)
             
             # If the class is guessed correctly, append the value to the correct_guesses list
             if  predicted== test_row[0]:

### 2019-09-13 src/main.py

@@ -97,7 +97,7 @@ print_database(db.get_data())
 # print('\n\n\n\n\nRunning classify_db():')
 temp_attr_headers = ['pol','a2','a3','a4','a5','a6','a7','a8','a9','a10','a11','a12','a13','a14','a15','a16','a17']
 binned_data = classifier.separate_data(temp_attr_headers,db.get_data())
-k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1])
+k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db)
 
 # classified_data = classifier.classify_db(temp_attr_headers, repaired_db, 0)
 

### 2019-09-13 src/database.py
Moved data shuffle function out of DB.

@@ -53,26 +53,26 @@ class database:
         return -1
     
     
-    def shuffle_all(self, percent):
-        if len(self.data) > 0:
+    def shuffle_all(training_data, percent):
+        if len(training_data) > 0:
             attribute_count = 0
-            for attribute in self.data[0]:
-                self.shuffle_data(percent, attribute_count)
+            for attribute in training_data[0]:
+                shuffle_data(percent, attribute_count)
                 attribute_count += 1
         
     
     # Shuffles X% of the data for an attribute specified by row of dataset.
-    def shuffle_data(self, percent, attribute):
+    def shuffle_data(training_data, percent, attribute):
         
         shuffling = []
         
         if(percent <= 100):
-            num_to_shuffle = int(len(self.data) * percent)
+            num_to_shuffle = int(len(training_data) * percent)
             
             # Will need to pull X% of the rows out of the database at random
             for iter in range(0, num_to_shuffle):
-                data_row = random.choice(self.data)
-                self.data.remove(data_row)
+                data_row = random.choice(training_data)
+                training_data.remove(data_row)
                 
                 # Adds the row data to be shuffled.
                 shuffling.append(data_row)
@@ -83,7 +83,7 @@ class database:
             
             # Sets the first row's attribute equal to the last row's.
             shuffling[0][attribute] = last_attribute
-            self.data.append(shuffling.pop(0))
+            training_data.append(shuffling.pop(0))
             
             # Shuffles remaining data
             for data_row in shuffling:
@@ -91,7 +91,7 @@ class database:
                 data_row[attribute] = temp_attribute
                 temp_attribute = temp
             
-            self.data += shuffling
+            training_data += shuffling
             print("Data Shuffled by",(percent*100),"%")
         else:
             print("ERROR: can't shuffle more than the size of the database.")

### 2019-09-13 src/process_data.py

@@ -216,3 +216,47 @@ def bootstrap_selection(normal_data, malformed_row, missing_data_val):
             corrected_data.append(malformed_row[index])
             
     return corrected_data
+
+
+def shuffle_all(training_data, percent):
+        if len(training_data) > 0:
+            attribute_count = 0
+            for attribute in training_data[0]:
+                shuffle_data(percent, attribute_count)
+                attribute_count += 1
+        
+    
+# Shuffles X% of the data for an attribute specified by row of dataset.
+def shuffle_data(training_data, percent, attribute):
+    
+    shuffling = []
+    
+    if(percent <= 100):
+        num_to_shuffle = int(len(training_data) * percent)
+        
+        # Will need to pull X% of the rows out of the database at random
+        for iter in range(0, num_to_shuffle):
+            data_row = random.choice(training_data)
+            training_data.remove(data_row)
+            
+            # Adds the row data to be shuffled.
+            shuffling.append(data_row)
+        
+        # Now we shift all the attribute's in the column specified down one from the randomly generated shuffle list.
+        last_attribute = shuffling[-1][attribute]
+        temp_attribute = shuffling[0][attribute]
+        
+        # Sets the first row's attribute equal to the last row's.
+        shuffling[0][attribute] = last_attribute
+        training_data.append(shuffling.pop(0))
+        
+        # Shuffles remaining data
+        for data_row in shuffling:
+            temp = data_row[attribute]
+            data_row[attribute] = temp_attribute
+            temp_attribute = temp
+        
+        training_data += shuffling
+        print("Data Shuffled by",(percent*100),"%")
+    else:
+        print("ERROR: can't shuffle more than the size of the database.")

### 2019-09-13 src/loss_functions.py
Implement cross entropy loss function

@@ -5,6 +5,16 @@ import os
 import process_data
 from path_manager import pathManager as pm
 
+""" -------------------------------------------------------------
+@param  prob  The probability of the guessed attribute value being correct
+              given the likelihood provided by the given attributes' conditional probabilities
+
+@return       The negative natural logarithm of @param prob
+@brief        An implementation of a cross entropy loss function
+"""
+def cross_entropy(prob):
+    return -np.log(prob)
+
 # Get true positive guesses
 def true_positives(bin_results, classes):
     correct = bin_results[1]

### 2019-09-13 src/database.py
Added get_classifiers() to database.py and incorporated my loss funcs into k_fold

@@ -52,6 +52,14 @@ class database:
         print("Error, class attribute not automatically located.")
         return -1
     
+    def get_classifiers(self):
+        class_idx = self.get_classifier_col()
+        classifiers = []
+        for row in self.data:
+            if row[class_idx] not in classifiers:
+                classifiers.append(row[class_idx])
+        
+        return classifiers
     
     def shuffle_all(self, percent):
         if len(self.data) > 0:

### 2019-09-13 src/k_fold_cross_validation.py

@@ -18,6 +18,7 @@ def k_fold(k,binned_data_set,bin_lengths, db):
     #print (binned_data_set)
     binned_guess_results = []
     attr_headers = db.get_attr()
+    class_list = db.get_classifiers()
     # For each bin in our data
     for bin_number in range(k):
         incorrect_guesses = []
@@ -59,8 +60,11 @@ def k_fold(k,binned_data_set,bin_lengths, db):
         print('\n \n \n Incorrect Guesses: \n \n')
         print(len(incorrect_guesses))
         print(" \n \n \n training probs \n \n \n" + str(training_probs))
-        # precision_non_binary()
-        # recall_non_binary()
+        print("BIN: ", [incorrect_guesses, correct_guesses])
+        precision = precision_non_binary([incorrect_guesses, correct_guesses], class_list)
+        recall = recall_non_binary([incorrect_guesses, correct_guesses], class_list)
+        print("PRECISION: ", precision)
+        print("PRECISION: ", recall)
 
 
     print(binned_guess_results)

### 2019-09-13 src/loss_functions.py

@@ -1,6 +1,5 @@
 import numpy as np
 from classifier import *
-from k_fold_cross_validation import *
 import os
 import process_data
 from path_manager import pathManager as pm

### 2019-09-13 src/main.py

@@ -99,6 +99,7 @@ temp_attr_headers = ['pol','a2','a3','a4','a5','a6','a7','a8','a9','a10','a11','
 binned_data = classifier.separate_data(temp_attr_headers,db.get_data())
 k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db)
 
+
 # classified_data = classifier.classify_db(temp_attr_headers, repaired_db, 0)
 
 # print(classified_data)

### 2019-09-13 src/classifier.py
Auto stash before merge of "master" and "origin/master"

@@ -220,7 +220,7 @@ def predict(probs, attrs, data_to_predict, db):
     classes = []
     for key in probs.keys():
         probs_products.append(1)
-
+    print(probs_products)
     for class_idx, data_class in enumerate(probs):
         classes.append(data_class)
         for attribute_idx in attribute_indexes:

### 2019-09-13 src/k_fold_cross_validation.py

@@ -37,30 +37,28 @@ def k_fold(k,binned_data_set,bin_lengths, db):
             training_data[row_idx2].pop(0)
 
         # Classify our training data set, so we can calculate the probabilites
-        classified_training_data = classifier.classify_db(attr_headers, training_data, 0)
+        classified_training_data = classifier.classify_db(attr_headers, training_data, db.get_classifier_col())
 
         # Calculate the probabilities
         training_probs = classifier.calc_prob_of_response(classified_training_data)
-
+        #print('\n \n \n Training Probs: \n \n \n')
+        #print(training_probs)
         # For each row (sample) in our test_data, try to predict its class
         for test_row in test_data:
             predicted = classifier.predict(training_probs, attr_headers, test_row, db)
             
             # If the class is guessed correctly, append the value to the correct_guesses list
-            if  predicted== test_row[0]:
+            if  predicted== test_row[db.get_classifier_col()]:
                 correct_guesses.append(predicted)
             # If the class is guessed incorrectly, append both the expected and predicted value to the incorrect_guesses list
             else:
-                incorrect_guesses.append([test_row[0],predicted])
+                incorrect_guesses.append([test_row[db.get_classifier_col()],predicted])
                 
         binned_guess_results.append([incorrect_guesses,correct_guesses])
-        print('\n \n \n Correct Guesses: \n \n')
-        print(len(correct_guesses))
-        print('\n \n \n Incorrect Guesses: \n \n')
-        print(len(incorrect_guesses))
-        print(" \n \n \n training probs \n \n \n" + str(training_probs))
-        # precision_non_binary()
-        # recall_non_binary()
-
-
-    print(binned_guess_results)
+        #print('\n \n \n Correct Guesses: \n \n')
+        #print(len(correct_guesses))
+        #print('\n \n \n Incorrect Guesses: \n \n')
+        #print(len(incorrect_guesses))
+        
+    #print(" \n \n \n Binned Guess Results\n \n \n")
+    #print(binned_guess_results)

### 2019-09-13 src/main.py

@@ -84,8 +84,8 @@ db.set_data(repaired_db)
 
 process_data.convert(db.get_data())
 
-print("\n\n\nFINAL DATABASE:\n\n\n")
-print_database(db.get_data())
+#print("\n\n\nFINAL DATABASE:\n\n\n")
+#print_database(db.get_data())
 # # -------------------------------------------------------------
 
 # print("\nRunning classifier...")
@@ -104,4 +104,4 @@ k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db)
 # print(probs)
 # print('\n\nprobs Products:\n')
 # print(classifier.predict(probs,['a2'],temp_attr_headers,repaired_db[0]))
-# print("\nFinished.")
+print("\nFinished.")

### 2019-09-13 src/classifier.py
Updated some stuff

@@ -220,11 +220,15 @@ def predict(probs, attrs, data_to_predict, db):
     classes = []
     for key in probs.keys():
         probs_products.append(1)
-    print(probs_products)
+    
     for class_idx, data_class in enumerate(probs):
         classes.append(data_class)
         for attribute_idx in attribute_indexes:
             if attribute_idx != db.get_classifier_col():
-                probs_products[class_idx] *= probs[data_class][attrs[attribute_idx]][data_to_predict[attribute_idx]][1]
+                print(probs[data_class][attrs[attribute_idx]][data_to_predict[attribute_idx]])
+                if probs[data_class][attrs[attribute_idx]][data_to_predict[attribute_idx]][1] != {}:
+                    probs_products[class_idx] *= probs[data_class][attrs[attribute_idx]][data_to_predict[attribute_idx]][1]
+                else:
+                    probs_products[class_idx] *= 0
     return classes[probs_products.index(max(probs_products))]
 

### 2019-09-13 src/main.py

@@ -52,8 +52,7 @@ path_manager.set_current_selected_folder(selected_database)
 # Processes the file path of the database into a pre processed database ready to be used as a learning/training set.
 db = process_data.process_database_file(path_manager)
 
-print("ATTRIBU{TES:}", db.get_attr())
-print(db.get_classifier_attribute_index())
+print("ATTRIBUTES:", db.get_attr())
 # ### Sanity checks. TODO: move to a unit test case file.
 normal_data, irregular_data = process_data.identify_missing_data(db)
 

### 2019-09-13 src/classifier.py
Fixed soybean data, commented some stuff, fixed some other hard code err

@@ -68,11 +68,16 @@ def classify_db(attrs, db, class_idx):
 
         # For each attribute in the current row..
         for attr_idx in range(len(row)):
-
+            
             # If the current attribute isn't the "class" attribute or the class's count...
             if attr_idx != class_idx and row[attr_idx] != 'count':
                 # If the current attribute isn't already in
                 # the data_tbl for the current class...
+                print(row)
+                print(len(attrs))
+                print(attr_idx)
+                print(attrs[attr_idx])
+                
                 if row[attr_idx] not in data_tbl[row[class_idx]][attrs[attr_idx]]:
                     # Make the current attribute a key for the current class
                     # and make that attribute's response count

### 2019-09-13 src/database.py

@@ -41,57 +41,3 @@ class database:
     def get_missing_symbol(self):
         return self.missing_symbol
     
-    def get_classifier_attribute_index(self):
-        index = 0
-        for attribute in self.attributes:
-            if "(class attribute)" in attribute:
-                print("HERE:", attribute)
-                return index
-            index+=1
-            
-        print("Error, class attribute not automatically located.")
-        return -1
-    
-    
-    def shuffle_all(training_data, percent):
-        if len(training_data) > 0:
-            attribute_count = 0
-            for attribute in training_data[0]:
-                shuffle_data(percent, attribute_count)
-                attribute_count += 1
-        
-    
-    # Shuffles X% of the data for an attribute specified by row of dataset.
-    def shuffle_data(training_data, percent, attribute):
-        
-        shuffling = []
-        
-        if(percent <= 100):
-            num_to_shuffle = int(len(training_data) * percent)
-            
-            # Will need to pull X% of the rows out of the database at random
-            for iter in range(0, num_to_shuffle):
-                data_row = random.choice(training_data)
-                training_data.remove(data_row)
-                
-                # Adds the row data to be shuffled.
-                shuffling.append(data_row)
-            
-            # Now we shift all the attribute's in the column specified down one from the randomly generated shuffle list.
-            last_attribute = shuffling[-1][attribute]
-            temp_attribute = shuffling[0][attribute]
-            
-            # Sets the first row's attribute equal to the last row's.
-            shuffling[0][attribute] = last_attribute
-            training_data.append(shuffling.pop(0))
-            
-            # Shuffles remaining data
-            for data_row in shuffling:
-                temp = data_row[attribute]
-                data_row[attribute] = temp_attribute
-                temp_attribute = temp
-            
-            training_data += shuffling
-            print("Data Shuffled by",(percent*100),"%")
-        else:
-            print("ERROR: can't shuffle more than the size of the database.")

### 2019-09-13 src/main.py

@@ -89,8 +89,7 @@ process_data.convert(db.get_data())
 
 # print("\nRunning classifier...")
 # print('\n\n\n\n\nRunning classify_db():')
-temp_attr_headers = ['pol','a2','a3','a4','a5','a6','a7','a8','a9','a10','a11','a12','a13','a14','a15','a16','a17']
-binned_data = classifier.separate_data(temp_attr_headers,db.get_data())
+binned_data = classifier.separate_data(db.get_attr(),db.get_data())
 k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db)
 
 # classified_data = classifier.classify_db(temp_attr_headers, repaired_db, 0)

### 2019-09-13 paper/paper.tex
Added to paper

@@
 
-\jmlrheading{1}{2000}{1-48}{4/00}{10/00}{Marina Meil\u{a} and Michael I. Jordan}
+\jmlrheading{1}{2019}{1-10}{9/19}{9/19}{George Engel, Troy Oster, Dana Parker, Henry Soule}
 
@@
 
-\editor{}
+\editor{Engel et al.}
 
@@
 
-Text goes here.
+A brief, one paragraph abstract summarizing the results of the experiments
 % Original text:
@@
 
-Intro goes here.
+Problem statement, including hypothesis
+
+\section{Problem Statement}
+
+\section{Algorithm}
+Per the instructions of the assignment, we implemented the naive Bayes algorithm on the five provided datasets.
+Given some example $x \in X$, where $X$ is our dataset, naive Bayes predicts the correct class $c$ of $x$ by computing the probabilities of each possible classification for $x$.
+For class $c$, the probability is denoted as follows: $P(c | a_1, a_2,...,a_d)$ where $a_k$ denotes one of $d$ attribute values in $x$.
+To compute this probability for each class $c$, the probabilities of each attribute value are computed.
+The
 

### 2019-09-13 src/database.py
Auto stash before merge of "master" and "origin/master"

@@ -40,4 +40,3 @@ class database:
     
     def get_missing_symbol(self):
         return self.missing_symbol
-    

### 2019-09-13 src/k_fold_cross_validation.py
Added code to get average precision and recall values.

@@ -19,6 +19,8 @@ def k_fold(k,binned_data_set,bin_lengths, db):
     binned_guess_results = []
     attr_headers = db.get_attr()
     class_list = db.get_classifiers()
+    precision_values = []
+    recall_values = []
     # For each bin in our data
     for bin_number in range(k):
         incorrect_guesses = []
@@ -60,6 +62,12 @@ def k_fold(k,binned_data_set,bin_lengths, db):
         #print(len(correct_guesses))
         #print('\n \n \n Incorrect Guesses: \n \n')
         #print(len(incorrect_guesses))
+        recall_values.append(recall_non_binary([incorrect_guesses, correct_guesses], class_list))
+        precision_values.append(precision_non_binary([incorrect_guesses,correct_guesses], class_list))
+        print("PRECISION: ", sum(precision_values) / len(precision_values))
+        print("RECALL: ", sum(recall_values) / len(recall_values))
+
+
         
     #print(" \n \n \n Binned Guess Results\n \n \n")
     #print(binned_guess_results)

### 2019-09-13 paper/paper.tex
Made progress on paper
Paper progress

@@
 \usepackage{jmlr2e}
+\usepackage{amsmath}
 
@@
 
-\section{Algorithm}
+\section{The Algorithm}
 Per the instructions of the assignment, we implemented the naive Bayes algorithm on the five provided datasets.
 Given some example $x \in X$, where $X$ is our dataset, naive Bayes predicts the correct class $c$ of $x$ by computing the probabilities of each possible classification for $x$.
-For class $c$, the probability is denoted as follows: $P(c | a_1, a_2,...,a_d)$ where $a_k$ denotes one of $d$ attribute values in $x$.
+For class $c$, the probability is denoted as $P(c | a_1, a_2,...,a_d)$ where $a_k$ denotes one of $d$ attribute values in $x$.
 To compute this probability for each class $c$, the probabilities of each attribute value are computed.
-The
+For each attribute value $a_k$, we compute $P(c) * \prod^d_{i=0} P(a_i | c)$, where $P(c)$ is the probability of an attribute being classified as class $c$.
+The predict the correct class for $x$ we compute $\underset{c \in C}{\mathrm{argmax}}$ $P(c) * \prod^d_{i=0} P(a_i | c)$.
+
+\section{Our Approach}
+% Preprocessing
+
+% Separating and classifying data
+To properly implement naive Bayes on the 5 datasets, we first needed to properly separate and classify each data set.
+Each data set needed to be separated by class, and then the count and probability of each attribute value for each class needed to be computed.
+Our approach for this was to create, for each dataset, an associative array, where each possible classifier was a key.
+For each key, the corresponding values were each their own associative arrays, the keys of which were all the extant attribute values among that class.
+The values of each key was a set storing the count and probability of each attribute value.
+
+% Shuffling(?)
+
+% Loss functions
+To assess the performance of our class prediction algorithm, we implemented two loss functions: Precision/Recall, and Cross Entropy.
+% Loss function 1: Precision Recall
+The Precision/Recall loss function computes two values, known as precision and recall, to measure the performance of our class prediction algorithm.
+This loss function utilizes the amounts of true positive, false positive, and false negative classifications for each class.
+Precision and recall are are computed as follows:
+$$Precision = \frac{1}{|C|} \sum^{|C|}_{i=1} \frac{TP_i}{TP_i + FP_i}$$
+$$Recall = \frac{1}{|C|} \sum^{|C|}_{i=1} \frac{TP_i}{TP_i + FN_i}$$
+$TP_i$ denotes the number of true positive classifications for class $i$, $FP_i$ denotes the number of false positive classifications for class $i$, and $FN_i$ denotes the number of false negative classifications for class $i$.
+$C$ is the set of all possible classes.
+Precision can be interpreted as a measure of how accurate true positive classifications, as it computes the fraction all positive classifications for a class that were truly positive.
+Recall measures accuracy among the values for each class that should have been positive, as it computes the fraction of all values that truly belonged to a class that were classified as positive.
+
+% Loss function 2: Cross Entropy
+\section{Results}
 

### 2019-09-13 src/classifier.py
Updated 0/1 loss

@@ -73,11 +73,6 @@ def classify_db(attrs, db, class_idx):
             if attr_idx != class_idx and row[attr_idx] != 'count':
                 # If the current attribute isn't already in
                 # the data_tbl for the current class...
-                print(row)
-                print(len(attrs))
-                print(attr_idx)
-                print(attrs[attr_idx])
-                
                 if row[attr_idx] not in data_tbl[row[class_idx]][attrs[attr_idx]]:
                     # Make the current attribute a key for the current class
                     # and make that attribute's response count
@@ -230,10 +225,9 @@ def predict(probs, attrs, data_to_predict, db):
         classes.append(data_class)
         for attribute_idx in attribute_indexes:
             if attribute_idx != db.get_classifier_col():
-                print(probs[data_class][attrs[attribute_idx]][data_to_predict[attribute_idx]])
                 if probs[data_class][attrs[attribute_idx]][data_to_predict[attribute_idx]][1] != {}:
                     probs_products[class_idx] *= probs[data_class][attrs[attribute_idx]][data_to_predict[attribute_idx]][1]
                 else:
-                    probs_products[class_idx] *= 0
+                    probs_products[class_idx] = 0
     return classes[probs_products.index(max(probs_products))]
 

### 2019-09-13 src/k_fold_cross_validation.py

@@ -1,6 +1,7 @@
 import classifier
 from copy import deepcopy
 from loss_functions import *
+import process_data
 
 """ -------------------------------------------------------------
 @param  k                   The number of folds we are using for k-fold cross validation
@@ -14,9 +15,10 @@ from loss_functions import *
            Then classify the training data and calculate the probabilities. Run prediction on each row of the test_data set and return an array of guess results containing guess results
            associated with each bin, as every bin will be the test bin at some point.
 """
-def k_fold(k,binned_data_set,bin_lengths, db):
+def k_fold(k,binned_data_set,bin_lengths, db, shuffle):
     #print (binned_data_set)
     binned_guess_results = []
+    percent_correct_bins = []
     attr_headers = db.get_attr()
     # For each bin in our data
     for bin_number in range(k):
@@ -36,6 +38,8 @@ def k_fold(k,binned_data_set,bin_lengths, db):
         for row_idx2 in range(len(training_data)):
             training_data[row_idx2].pop(0)
 
+        if shuffle:
+            training_data = process_data.shuffle_all(training_data,.1)
         # Classify our training data set, so we can calculate the probabilites
         classified_training_data = classifier.classify_db(attr_headers, training_data, db.get_classifier_col())
 
@@ -55,10 +59,10 @@ def k_fold(k,binned_data_set,bin_lengths, db):
                 incorrect_guesses.append([test_row[db.get_classifier_col()],predicted])
                 
         binned_guess_results.append([incorrect_guesses,correct_guesses])
-        #print('\n \n \n Correct Guesses: \n \n')
-        #print(len(correct_guesses))
-        #print('\n \n \n Incorrect Guesses: \n \n')
-        #print(len(incorrect_guesses))
+        percent_correct_bins.append(len(correct_guesses)/(len(incorrect_guesses)+len(correct_guesses)))
+    
+    return sum(percent_correct_bins)/len(percent_correct_bins)
+    
         
     #print(" \n \n \n Binned Guess Results\n \n \n")
     #print(binned_guess_results)

### 2019-09-13 src/main.py

@@ -90,7 +90,10 @@ process_data.convert(db.get_data())
 # print("\nRunning classifier...")
 # print('\n\n\n\n\nRunning classify_db():')
 binned_data = classifier.separate_data(db.get_attr(),db.get_data())
-k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db)
+print('\n \n \n Pre-shuffle 0/1 loss: ')
+print(k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, False))
+print('\n \n \n Post-shuffle 0/1 loss: ')
+print(k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, True))
 
 # classified_data = classifier.classify_db(temp_attr_headers, repaired_db, 0)
 

### 2019-09-13 paper/paper.tex

--- 2019-09-13 paper/paper.tex
@@
 Given some example $x \in X$, where $X$ is our dataset, naive Bayes predicts the correct class $c$ of $x$ by computing the probabilities of each possible classification for $x$.
-For class $c$, the probability is denoted as follows: $P(c | a_1, a_2,...,a_d)$ where $a_k$ denotes one of $d$ attribute values in $x$.
+For class $c$, the probability is denoted as $P(c | a_1, a_2,...,a_d)$ where $a_k$ denotes one of $d$ attribute values in $x$.
 To compute this probability for each class $c$, the probabilities of each attribute value are computed.
-The
+For each attribute value $a_k$, we compute $P(c) * \prod^d_{i=0} P(a_i | c)$, where $P(c)$ is the probability of an attribute being classified as class $c$.
+The predict the correct class for $x$ we compute $\DeclareMath
 

### 2019-09-13 paper/paper.tex
Working on paper

--- 2019-09-13 paper/paper.tex
@@
 \section{Problem Statement}
+For this assignment, we were provided with 5 real world datasets.
+In each dataset, all data points were comprised of both quantitative and categorical variables, and each dataset had a designated classification.
+Our task was to train an algorithm to predict the classification of a given datapoint.
+Our algorithm was trained by computing probabilities of each unique attribute value among the different classifications within each dataset, and then use to these probabilities to predict the classification of any datapoint.
+We then implemented two loss functions to measure the accuracy of our prediction algorithm.
 
@@
 % Loss functions
-To assess the performance of our class prediction algorithm, we implemented two loss functions: Precision/Recall, and Cross Entropy.
+To assess the performance of our class prediction algorithm, we implemented two loss functions: Precision/Recall, and 0/1 Loss.
 % Loss function 1: Precision Recall
@@
 Precision can be interpreted as a measure of how accurate true positive classifications, as it computes the fraction all positive classifications for a class that were truly positive.
-Recall measures accuracy among the values for each class that should have been positive, as it computes the fraction of all values that truly belonged to a class that were classified as positive.
+Recall measures accuracy among the values for each class that should have been positive, as it computes the fraction of all values that truly belonged to a class that were classified as positive[1].
 
@@
 
-\acks{Acknowledgements go here.}
+\acks{
+
+Davis, Jesse, and Mark Goadrich.
+"The Relationship between Precision-Recall and ROC Curves." Proceedings of the 23rd International Conference on Machine Learning - ICML 06, 2006, doi:10.1145/1143844.1143874.
+
+}
 

### 2019-09-13 src/k_fold_cross_validation.py
Put precision and recall print statments where they belong.

@@ -64,10 +64,10 @@ def k_fold(k,binned_data_set,bin_lengths, db, shuffle):
         binned_guess_results.append([incorrect_guesses,correct_guesses])
         recall_values.append(recall_non_binary([incorrect_guesses, correct_guesses], class_list))
         precision_values.append(precision_non_binary([incorrect_guesses,correct_guesses], class_list))
-        print("PRECISION: ", sum(precision_values) / len(precision_values))
-        print("RECALL: ", sum(recall_values) / len(recall_values))
         percent_correct_bins.append(len(correct_guesses)/(len(incorrect_guesses)+len(correct_guesses)))
     
+    print("PRECISION: ", sum(precision_values) / len(precision_values))
+    print("RECALL: ", sum(recall_values) / len(recall_values))
     return sum(percent_correct_bins)/len(percent_correct_bins)
     
         

### 2019-09-13 src/loss_functions.py
Fixed division by 0 error

@@ -52,8 +52,10 @@ def precision_non_binary(bin_results, classes):
     precision = 0
     
     for i in range(len(TP)):
-        precision += TP[i] / (TP[i] + FP[i])
-    
+        if TP[i] == 0 and FP[i] == 0:
+            precision += 0
+        else:
+            precision += TP[i] / (TP[i] + FP[i])
     return  (1 / len(TP)) * precision
 
 '''----------------------------------------
@@ -67,7 +69,10 @@ def recall_non_binary(bin_results, classes):
     recall = 0
     
     for i in range(len(TP)):
-        recall += TP[i] / (TP[i] + FN[i])
+        if FN[i] == 0 and TP[i] == 0:
+            recall += 0
+        else:
+            recall += TP[i] / (TP[i] + FN[i])
     
     return (1 / len(TP)) * recall
 

### 2019-09-13 src/k_fold_cross_validation.py
more optimizations

@@ -65,7 +65,8 @@ def k_fold(k,binned_data_set,bin_lengths, db, shuffle):
         recall_values.append(recall_non_binary([incorrect_guesses, correct_guesses], class_list))
         precision_values.append(precision_non_binary([incorrect_guesses,correct_guesses], class_list))
         percent_correct_bins.append(len(correct_guesses)/(len(incorrect_guesses)+len(correct_guesses)))
-    
+    print("CORRECT GUESSED:", correct_guesses)
+    print("WRONG GUESSES:", incorrect_guesses)
     print("PRECISION: ", sum(precision_values) / len(precision_values))
     print("RECALL: ", sum(recall_values) / len(recall_values))
     return sum(percent_correct_bins)/len(percent_correct_bins)

### 2019-09-13 src/main.py

@@ -56,8 +56,8 @@ db = process_data.process_database_file(path_manager)
 normal_data, irregular_data = process_data.identify_missing_data(db)
 
 corrected_data = process_data.extrapolate_data(normal_data, irregular_data, db.get_missing_symbol())
-print("\nNormal Data:")
-print_database(normal_data)
+# print("\nNormal Data:")
+# print_database(normal_data)
 
 # -------------------------------------------------------------
 

### 2019-09-13 src/k_fold_cross_validation.py
optimized glass

@@ -65,8 +65,6 @@ def k_fold(k,binned_data_set,bin_lengths, db, shuffle):
         recall_values.append(recall_non_binary([incorrect_guesses, correct_guesses], class_list))
         precision_values.append(precision_non_binary([incorrect_guesses,correct_guesses], class_list))
         percent_correct_bins.append(len(correct_guesses)/(len(incorrect_guesses)+len(correct_guesses)))
-    print("CORRECT GUESSED:", correct_guesses)
-    print("WRONG GUESSES:", incorrect_guesses)
     print("PRECISION: ", sum(precision_values) / len(precision_values))
     print("RECALL: ", sum(recall_values) / len(recall_values))
     return sum(percent_correct_bins)/len(percent_correct_bins)

### 2019-09-13 src/k_fold_cross_validation.py
Auto stash before merge of "master" and "origin/master"

@@ -65,6 +65,7 @@ def k_fold(k,binned_data_set,bin_lengths, db, shuffle):
         recall_values.append(recall_non_binary([incorrect_guesses, correct_guesses], class_list))
         precision_values.append(precision_non_binary([incorrect_guesses,correct_guesses], class_list))
         percent_correct_bins.append(len(correct_guesses)/(len(incorrect_guesses)+len(correct_guesses)))
+        
     print("PRECISION: ", sum(precision_values) / len(precision_values))
     print("RECALL: ", sum(recall_values) / len(recall_values))
     return sum(percent_correct_bins)/len(percent_correct_bins)

### 2019-09-13 paper/paper.tex
Paper stuff

--- 2019-09-13 paper/paper.tex
@@
 A brief, one paragraph abstract summarizing the results of the experiments
-% Original text:
-% This paper describes the mixtures-of-trees model, a probabilistic 
-% model for discrete multidimensional domains.  Mixtures-of-trees 
-% generalize the probabilistic trees of \citet{chow:68}
-% in a different and complementary direction to that of Bayesian networks.
-% We present efficient algorithms for learning mixtures-of-trees 
-% models in maximum likelihood and Bayesian frameworks. 
-% We also discuss additional efficiencies that can be
-% obtained when data are ``sparse,'' and we present data 
-% structures and algorithms that exploit such sparseness.
-% Experimental results demonstrate the performance of the 
-% model for both density estimation and classification. 
-% We also discuss the sense in which tree-based classifiers
-% perform an implicit form of feature selection, and demonstrate
-% a resulting insensitivity to irrelevant attributes.
+
 \end{abstract}
@@
 \section{Introduction}
-
-Problem statement, including hypothesis
+The naive Bayes classification model is a simple model for predicting data classification.
+In this assignment, we implemented this probabilistic model on multiple real-world datasets.
+We validated our implementation of the algorithm with 10-fold cross-validation and measured the performance of our implementation with two loss functions: 0-1 Loss, and Precision/Recall.
 
 \section{Problem Statement}
+Given a data set of which all the correct classifications are known, we can implement and execute a training algorithm on a subset of the data.
+Then, once trained, the algorithm will guess the classes of another subset of the data and measure the performance.
+For this assignment, we were provided with 5 real-world data sets.
+Our task was to implement a training algorithm and guess classifications for each of these 5 data sets and then utilize two different loss functions to measure the accuracy and performance of our predictions.
+We ran this algorithm on the original versions of each data set, and then introduced noise to each of the data sets by shuffling attribute values among 10\% of the values, and ran the algorithm of the five shuffled versions of the data.
+We hypothesized that we would acheive
 
 \section{The Algorithm}
-Per the instructions of the assignment, we implemented the naive Bayes algorithm on the five provided datasets.
-Given some example $x \in X$, where $X$ is our dataset, naive Bayes predicts the correct class $c$ of $x$ by computing the probabilities of each possible classification for $x$.
+Per the instructions of the assignment, we implemented the naive Bayes algorithm on the 5 provided data sets.
+Given some example $x \in X$, where $X$ is our data set, naive Bayes predicts the correct class $c$ of $x$ by computing the probabilities of each possible classification for $x$.
 For class $c$, the probability is denoted as $P(c | a_1, a_2,...,a_d)$ where $a_k$ denotes one of $d$ attribute values in $x$.
@@
 For each attribute value $a_k$, we compute $P(c) * \prod^d_{i=0} P(a_i | c)$, where $P(c)$ is the probability of an attribute being classified as class $c$.
-The predict the correct class for $x$ we compute $\underset{c \in C}{\mathrm{argmax}}$ $P(c) * \prod^d_{i=0} P(a_i | c)$.
+To predict the correct class for $x$ we compute $\underset{c \in C}{\mathrm{argmax}}$ $P(c) * \prod^d_{i=0} P(a_i | c)$.
 
@@
 % Separating and classifying data
-To properly implement naive Bayes on the 5 datasets, we first needed to properly separate and classify each data set.
+To properly implement naive Bayes on the 5 data sets, we first needed to properly separate and classify each data set.
 Each data set needed to be separated by class, and then the count and probability of each attribute value for each class needed to be computed.
@@
 For each key, the corresponding values were each their own associative arrays, the keys of which were all the extant attribute values among that class.
-The values of each key was a set storing the count and probability of each attribute value.
-
+The value of each key in these inner arrays was a set storing the count and conditional probability of each attribute value given the respective class.
+\\ \\
 % Shuffling(?)
-
+%K-Fold Cross Validation
+We tested our algorithm's implementation using 10-fold cross-validation.
+This validation model separates each data set into 10 subsets, or "bins", of equal size.
+It then runs 10 iterations.
+During each iteration, one bin is designated as the test data, being the data we will test our prediction algorithm on.
+The other 9 bins are designated as training data.
+It is on this training data subset that we will execute our learning algorithm, from which we will base our predictions.
+After first running the training algorithm on these 9 bins, we then predict the classifications of each example in the designated test data.
+For each iteration, a different bin is designated as test data, while the other 9 are designated as the training data.
+\\ \\
 % Loss functions
-To assess the performance of our class prediction algorithm, we implemented two loss functions: Precision/Recall, and Cross Entropy.
+To assess the performance of our class prediction algorithm, we implemented two loss functions: Precision/Recall, and 0-1 Loss.
+We ran both loss functions on each iteration of the 10-fold cross-validation process, and then took averages of the values returned during from each iteration and used these values to measure the performance of our prediction algorithm.
+0-1 Loss simply computes the fraction of the data our algorithm correctly classified.
+For each correctly classified data example, a 0 is returned, and for every incorrectly classified value, a 1 is returned.
+Accuracy is then defined as the percentage of 0's returned [2].\\ \\
 % Loss function 1: Precision Recall
@@
 $C$ is the set of all possible classes.
-Precision can be interpreted as a measure of how accurate true positive classifications, as it computes the fraction all positive classifications for a class that were truly positive.
-Recall measures accuracy among the values for each class that should have been positive, as it computes the fraction of all values that truly belonged to a class that were classified as positive.
+Precision can be interpreted as a measure of how accurate true positive classifications are, as it computes the fraction of all positive classifications for a class that were truly positive.
+Recall measures accuracy among the values for each class that should have been positive, as it computes the fraction of all values that truly belonged to a class that were classified as positive [1].
+\\ \\
 
-% Loss function 2: Cross Entropy
 \section{Results}
@@
 
-\acks{Acknowledgements go here.}
+\acks{1.
+Davis, Jesse, and Mark Goadrich.
+"The Relationship between Precision-Recall and ROC Curves." Proceedings of the 23rd International Conference on Machine Learning - ICML 06, 2006, doi:10.1145/1143844.1143874.
+\\ \\
+2.
+Dietterich, Thomas G.
+"Machine Learning for Sequential Data: A Review." Lecture Notes in Computer Science Structural, Syntactic, and Statistical Pattern Recognition, 2002, pp.
+15-30., doi:10.1007/3-540-70659-32.}
 

### 2019-09-13 classifier.py
Code cleanup

@@ -1,38 +1,0 @@
-
-import numpy as np
-
-def separateData(attributes, data, attToClassify):
-    """
-    [[1,2,3],[1,2,3]]
-    """
-    # attributes: ["Foo"..."Bar"]
-    # data: [[1,2,3],[1,2,3]]
-    # attToClassify: "Foo", A string matching the column name, or attribute, of the dataset
-    # Creating a dictionary to hold the class types
-    indexOfAttribute = attributes.index(attToClassify)
-    dataClasses = {}
-    for i in range(len(data)):
-        example = data[i]
-        if example[indexOfAttribute] not in dataClasses:
-            dataClasses[example[indexOfAttribute]] = []
-        dataClasses[example[indexOfAttribute]].append(example)
-    return dataClasses
-
-
-def attributeCount(subset): #TODO find a better name for this function
-    # get dimensions of subset
-    rows, cols = subset.shape
-    for col in subset.T:
-        for val in col:
-            # https://ask.sagemath.org/question/10279/frequency-count-in-numpy-array/
-            # got this count method from above link
-            count = list(col).count(val)
-            print(val, ': ', count) 
-        print('----------')
-    # for a in attributes:
-    #     getCount(a, subset)
-
-
-def getCount(attribute, data):
-    return 1
-

### 2019-09-13 src/classifier.py

@@ -84,42 +84,11 @@ def classify_db(attrs, db, class_idx):
     # Return the completed data structure per the form in @return
     return data_tbl
 
-# """ -------------------------------------------------------------
-# Calculate probabilities for each attribute value
-# This is step 2 in the algorithm
-# @param data_tbl a data_table created by the classify_db() function
-# """
-# def calculate_probs(data_tbl):
-    # Iterate over each class in data_tbl
-    # for classifier, values in data_tbl.items():
-    #     for val in values:
-    #         if val != 'count':
-    #             # Loop thru each value count and calculate the probabilities
-    #             for count in data_tbl[classifier][val]:
-    #                 data_tbl[classifier][val][count][1] = data_tbl[classifier][val][count][0] / data_tbl[classifier]['count']
-
-
-# -------------------------------------------------------------
-# Old function to calculate attribute probabilities.
-# Used the genDataTable function that we no longer have
-# 
-# import copy
-# def calculate_attr_probs(data, attributes, attr_to_classify):
-#     # classified_data = separate_data(attributes, data, attr_to_classify)['class']
-#     data_table = classify_db(attributes, data, attr_to_classify)
-#     prob_table = copy.deepcopy(data_table)
-#     for classifier, count_list in prob_table.items():
-#         for val, val_counts in count_list.items():
-#             for val, count in val_counts.items():
-#                 prob = (count + 1) / (len(classified_data[classifier]) + len(attributes))
-#                 val_counts[val] = prob
-
-#     return prob_table
-
 '''--------------------------------------------------------------
-Calculate proportions/probabilities of each class within the data set
-@param data - The data Tree, with the class counts included
-@return a set containing the probabilities for each class
+@param     data    The data Tree, with the class counts included
+
+@return     A set containing the probabilities for each class
+@brief      Calculate proportions/probabilities of each class within the data set
 '''
 def get_class_probs(data):
     Q = [] # Set to store class probs
@@ -133,39 +102,38 @@ def get_class_probs(data):
     Q = [x / total_data for x in Q]
     return Q
 
-''' -------------------------------------------------------------
-Guess the class of an example
-@param  example a row from the test set that we are trying to classify
-@param  tbd     the training data table
-@param  class_idx   the index of the column that stores the class for each row in the data
-@return the predicted class
-'''
-import numpy as np
-def calculate_class(example, tbd, class_probs, class_idx):
-    # print("Example: ", example)
[…]

### 2019-09-13 src/classifier_testing.py

@@ -1,35 +1,0 @@
-import classifier
-# from classifier import genDataTable
-import os
-import process_data
-from path_manager import pathManager as pm
-
-
-# dataset = [["y","n","Democrat"], ["n","y","Republican"], ["n","n","Democrat"]]
-# print(separate_data(["q1","q2", "Classes"],dataset,"Classes"))
-# print(genDataTable(["q1","q2", "Classes"],dataset,"Classes"))
-
-# Prepare iris database for testing purposes
-full_path = "/Users/admin/Desktop/2019 Fall Semester/Machine Learning/CSCI-447-Project-1/databases/iris/iris.data"
-db = process_data.process_database_file(full_path)
-
-normal_data, irregular_data = process_data.identify_missing_data(db.get_data(), 'sepal width in cm')
-normal_data = normal_data[0:len(normal_data)-1] # last row is empty so the code wasn't running
-
-attrs = ["sepal length", "sepal width", "petal length", "petal width", "class"]
-# classified_data = separate_data(attrs, normal_data, "class")['class']
-classified_data = classifier.classify_db(attrs, normal_data, 4)
-classified_data = classifier.calc_prob_of_response(classified_data)
-
-classifier.calculate_class(normal_data[0], classified_data, 4)
-
-
-
-
-
-
-
-
-
-
-

### 2019-09-13 src/db_testing.py

@@ -1,11 +1,0 @@
-from classifier import add_noise
-import os
-import process_data
-from path_manager import pathManager as pm
-
-
-# Prepare iris database for testing purposes
-full_path = "/Users/admin/Desktop/2019 Fall Semester/Machine Learning/CSCI-447-Project-1/databases/iris/iris.data"
-db = process_data.process_database_file(full_path)
-add_noise(db, 4)
-

### 2019-09-13 src/k_fold_cross_validation.py

@@ -1,3 +1,9 @@
+""" -------------------------------------------------------------
+@file        k_fold_cross_validation.py
+@authors     George Engel, Troy Oster, Dana Parker, Henry Soule
+@brief       Contains all functionality related to k-fold cross-validation
+"""
+
 import classifier
 from copy import deepcopy
 from loss_functions import *
@@ -11,9 +17,15 @@ import process_data
 @return    binned_guess_results: [[<incorrect_guesses>, <correct_guesses>]]
                 incorrect_guesses: [[expected answer,incorrect guess]]
                 correct_guesses: [correct guess] 
-@brief     Given a number of folds k, and binned data, as well as bin_lengths, iterate over each bin and separate the data into two subsets, training_data and test_data. 
-           Then classify the training data and calculate the probabilities. Run prediction on each row of the test_data set and return an array of guess results containing guess results
-           associated with each bin, as every bin will be the test bin at some point.
+
+@brief     Given a number of folds k, and binned data, as well as bin_lengths,
+           iterate over each bin and separate the data into two subsets, 
+           training data and test_data. 
+           Then classify the training data and calculate the probabilities.
+           Run prediction on each row of the test_data set and return
+           an array of guess results containing
+           guess results associated with each bin,
+           as every bin will be the test bin at some point.
 """
 def k_fold(k,binned_data_set,bin_lengths, db, shuffle):
     #print (binned_data_set)

### 2019-09-13 src/main.py

@@ -3,6 +3,7 @@
 @authors     George Engel, Troy Oster, Dana Parker, Henry Soule
 @brief       The file that runs the program
 """
+
 import os
 import process_data
 import classifier
@@ -52,25 +53,10 @@ path_manager.set_current_selected_folder(selected_database)
 # Processes the file path of the database into a pre processed database ready to be used as a learning/training set.
 db = process_data.process_database_file(path_manager)
 
-# ### Sanity checks. TODO: move to a unit test case file.
+# Sanity checks.
 normal_data, irregular_data = process_data.identify_missing_data(db)
 
 corrected_data = process_data.extrapolate_data(normal_data, irregular_data, db.get_missing_symbol())
-# print("\nNormal Data:")
-# print_database(normal_data)
-
-# -------------------------------------------------------------
-
-#print("\n\n\n\n\nIrregular Data:")
-#print_database(irregular_data)
-
-# -------------------------------------------------------------
-
-# print("\n\n\n\n\nCorrected Irregular Data:")
-# print_database(corrected_data)
-#print("Irregular data total:", len(irregular_data))
-#print("Regular data total:", len(normal_data))
-#rint("Corrected data total:", len(corrected_data))
 
 # repaired_db is the total database once the missing values have been filled in.
 if len(corrected_data) > 0:
@@ -82,13 +68,6 @@ db.set_data(repaired_db)
 
 process_data.convert(db.get_data())
 
-#print("\n\n\nFINAL DATABASE:\n\n\n")
-#print_database(db.get_data())
-# # -------------------------------------------------------------
-
-# print("\nRunning classifier...")
-# print('\n\n\n\n\nRunning classify_db():')
-
 binned_data = classifier.separate_data(db.get_attr(),db.get_data())
 print('\n \n Pre-shuffle')
 print('---------------------')
@@ -99,14 +78,4 @@ print('---------------------')
 post_shuffle = k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, True)
 print("0/1 Loss: ", post_shuffle)
 
-# classified_data = classifier.classify_db(temp_attr_headers, repaired_db, 0)
-
-# print(classified_data)
-
-# print("\n\nRunning calc_prob_of_response():")
-# probs = classifier.calc_prob_of_response(classified_data)
-# print('\n\nprobs:\n')
-# print(probs)
-# print('\n\nprobs Products:\n')
-# print(classifier.predict(probs,['a2'],temp_attr_headers,repaired_db[0]))
 print("\nFinished.")

### 2019-09-13 src/process_data.py

@@ -15,7 +15,7 @@ import os
             (see database.py)
 @brief      Loads the file contents into a database object
 """
-# FIXME: Change to use numpy for efficiency's sake?
+
 def process_database_file(path_manager):
 
     # loads in data file from the selected database directory
@@ -99,7 +99,6 @@ def needs_conversion(database, attribute_col):
 # Converts a column of quantitative data to catagorical values.
 def equal_width_conversion(database, attribute_col):
     
-    # TODO: Change bin count dynamically at some point?
     bin_count = 3
     
     min = float(database[0][attribute_col])
@@ -115,11 +114,10 @@ def equal_width_conversion(database, attribute_col):
     # Calculate binning width
     width = (max - min)/bin_count
 
-    # TODO: Change these bins from arbitrary to dynamic
     small_bin = []
     medium_bin = []
     large_bin = []
-    # Put stuff in bins
+    # Put data in bins
     for data_row in database:
         if min <= float(data_row[attribute_col]) < (min+width):
             small_bin.append(data_row)
@@ -143,16 +141,14 @@ def equal_width_conversion(database, attribute_col):
     
     return merged_bins
         
-    
-    
-    
-
 """ -------------------------------------------------------------
-@param  database        Input database to operate upon per @brief
-@param  attribute_count The amount of expected attributes for each row of data.
+@param  database           Input database to operate upon per @brief
+@param  attribute_count    The amount of expected attributes for each row of data.
 
-@return     input_db, correction_que : returns the 'clean' rows of data (input_db), and the rows of any malformed data (correction_queue).
-            PS: You aren't dumb Dana -George
+@return     input_db, correction_que :
+            returns the 'clean' rows of data (input_db),
+            and the rows of any malformed data (correction_queue).
+
 @brief      Either removes data with missing parameters,
             or extrapolates missing data using bootstraping methodology.
 """
@@ -197,12 +193,6 @@ def extrapolate_data(normal_data, malformed_data, missing_data_val):
         
     return corrected_data
     
-# Deal with missing attributes
-    # If 'low' number of missing attributes: remove.
-    # Else: Generate a random attribute from a pool of prexisting ones?
-        # Set up a queue of lines that need to do this, so we have the pool already fully generated.
-            # TODO: DOCUMENT THIS CHOICE.*/
-            
 # Fills in the unknown/missing data from existing normal data randomly.
 def bootstrap_selection(normal_data, malformed_row, missing_data_val):
     length = len(malformed_row)

### 2019-09-13 src/test.py

@@ -1,34 +1,0 @@
-""" -------------------------------------------------------------
-@file        main.py
-@authors     George Engel, Troy Oster, Dana Parker, Henry Soule
-@brief       The file that runs the program
-"""
-# TODO: Turn the contents of this file into unit tests.
-import process_data
-from path_manager import pathManager as pm
-
-# Cleaner print outs for the sake of my sanity.
-def print_database(database):
-    
-    if len(database) < 1:
-        print("[] - Empty")
-    else:
-        for row in database:
-            print(row)
-
-print("Starting...")
-# TODO: Enter user input for pathing. -George
-# TODO: Make pathing manager for choosing database -George
-db = process_data.process_database_file("../databases/breast-cancer-wisconsin/breast-cancer-wisconsin.data")
-
-normal_data, irregular_data = process_data.identify_missing_data(db.get_data())
-
-print("\nNormal Data:")
-print_database(normal_data)
-
-print("\nIrregular Data:")
-print_database(irregular_data)
-
-print("\nFinished.")
-
-test = pm()

### 2019-09-13 src/k_fold_cross_validation.py
Auto stash before merge of "master" and "origin/master"

@@ -80,7 +80,7 @@ def k_fold(k,binned_data_set,bin_lengths, db, shuffle):
         
     print("PRECISION: ", sum(precision_values) / len(precision_values))
     print("RECALL: ", sum(recall_values) / len(recall_values))
-    return sum(percent_correct_bins)/len(percent_correct_bins)
+    return [sum(percent_correct_bins)/len(percent_correct_bins), training_probs]
     
         
     #print(" \n \n \n Binned Guess Results\n \n \n")

### 2019-09-13 src/main.py

@@ -69,13 +69,20 @@ db.set_data(repaired_db)
 process_data.convert(db.get_data())
 
 binned_data = classifier.separate_data(db.get_attr(),db.get_data())
+print("\n \n Input Data Structure:")
+print('---------------------')
+print(db.get_data()[0:10])
 print('\n \n Pre-shuffle')
 print('---------------------')
 pre_shuffle = k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, False)
-print("0/1 Loss: ", pre_shuffle)
+print("0/1 Loss: ", pre_shuffle[0])
 print('\n \n Post-shuffle')
 print('---------------------')
 post_shuffle = k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, True)
+print("0/1 Loss: ", post_shuffle[0])
+print("\n \n Probability Data Structure:")
+print('---------------------')
+print(post_shuffle[1])
 print("0/1 Loss: ", post_shuffle)
 
 print("\nFinished.")

### 2019-09-13 src/k_fold_cross_validation.py
Final cleanup

@@ -60,8 +60,7 @@ def k_fold(k,binned_data_set,bin_lengths, db, shuffle):
 
         # Calculate the probabilities
         training_probs = classifier.calc_prob_of_response(classified_training_data)
-        #print('\n \n \n Training Probs: \n \n \n')
-        #print(training_probs)
+
         # For each row (sample) in our test_data, try to predict its class
         for test_row in test_data:
             predicted = classifier.predict(training_probs, attr_headers, test_row, db)
@@ -81,7 +80,3 @@ def k_fold(k,binned_data_set,bin_lengths, db, shuffle):
     print("PRECISION: ", sum(precision_values) / len(precision_values))
     print("RECALL: ", sum(recall_values) / len(recall_values))
     return sum(percent_correct_bins)/len(percent_correct_bins)
-    
-        
-    #print(" \n \n \n Binned Guess Results\n \n \n")
-    #print(binned_guess_results)

### 2019-09-13 src/process_data.py

@@ -40,7 +40,6 @@ def process_database_file(path_manager):
     
     attributes, classifier_column, classifier_attr_cols, missing_symbol = read_attributes(path_manager.get_current_selected_dir(), data_filename)
 
-    print(attributes)
     return db(db_data, attributes, classifier_column, classifier_attr_cols, missing_symbol)
 
 # Reads in the attribute file from a database, and returns the attributes as a list
@@ -92,7 +91,6 @@ def needs_conversion(database, attribute_col):
         try:
             float(data_row[attribute_col])
         except ValueError:
-            print("Not a float")
             return False
     return True
 

### 2019-09-13 src/classifier.py
Commented predict method

@@ -189,17 +189,22 @@ def calc_prob_of_response(db):
 @param  data_to_predict     Our test data subset
 @param  db                  Our training data subset
 """
+# This method predicts the class of the sample that it is given
 def predict(probs, attrs, data_to_predict, db):
     attribute_indexes = db.get_classifier_attr_cols()
     probs_products = []
     classes = []
+    #This appends 1 to the probabilites so that we can use *= later
     for key in probs.keys():
         probs_products.append(1)
-    
+    #For each key in the probability dictionary, this whole loop structure traverses the dictionary of probabilities
     for class_idx, data_class in enumerate(probs):
         classes.append(data_class)
+        #For each index in the list of indexes for the attributes
         for attribute_idx in attribute_indexes:
+            #This prevents us from calculating probabilities based on the class we are trying to predict
             if attribute_idx != db.get_classifier_col():
+                # This prevents errors when there are 0 instances where an attribute has a certain value
                 if probs[data_class][attrs[attribute_idx]][data_to_predict[attribute_idx]][1] != {}:
                     probs_products[class_idx] *= probs[data_class][attrs[attribute_idx]][data_to_predict[attribute_idx]][1]
                 else:

### 2019-09-13 src/main.py
Fixed main.py

@@ -69,20 +69,15 @@ db.set_data(repaired_db)
 process_data.convert(db.get_data())
 
 binned_data = classifier.separate_data(db.get_attr(),db.get_data())
-print("\n \n Input Data Structure:")
-print('---------------------')
-print(db.get_data()[0:10])
+
 print('\n \n Pre-shuffle')
 print('---------------------')
 pre_shuffle = k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, False)
-print("0/1 Loss: ", pre_shuffle[0])
+print("0/1 Loss: ", pre_shuffle)
 print('\n \n Post-shuffle')
 print('---------------------')
 post_shuffle = k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, True)
-print("0/1 Loss: ", post_shuffle[0])
-print("\n \n Probability Data Structure:")
-print('---------------------')
-print(post_shuffle[1])
 print("0/1 Loss: ", post_shuffle)
+
 
 print("\nFinished.")

### 2019-09-13 src/k_fold_cross_validation.py
Auto stash before merge of "master" and "origin/master"

@@ -77,6 +77,12 @@ def k_fold(k,binned_data_set,bin_lengths, db, shuffle):
         precision_values.append(precision_non_binary([incorrect_guesses,correct_guesses], class_list))
         percent_correct_bins.append(len(correct_guesses)/(len(incorrect_guesses)+len(correct_guesses)))
         
-    print("PRECISION: ", sum(precision_values) / len(precision_values))
-    print("RECALL: ", sum(recall_values) / len(recall_values))
-    return sum(percent_correct_bins)/len(percent_correct_bins)
+    PRECISION = sum(precision_values) / len(precision_values)
+    RECALL = sum(recall_values) / len(recall_values)
+    # print("PRECISION: ", sum(precision_values) / len(precision_values))
+    # print("RECALL: ", sum(recall_values) / len(recall_values))
+    return PRECISION, RECALL, (sum(percent_correct_bins)/len(percent_correct_bins))
+    
+        
+    #print(" \n \n \n Binned Guess Results\n \n \n")
+    #print(binned_guess_results)

### 2019-09-13 src/main.py

@@ -9,6 +9,9 @@ import process_data
 import classifier
 import k_fold_cross_validation
 from path_manager import pathManager as pm
+import xlwt
+from xlwt import Workbook
+import statistics
 
 # Asks for user to select a database from a list presented from current database collection directory.
 def select_database(databases):
@@ -79,5 +82,51 @@ print('---------------------')
 post_shuffle = k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, True)
 print("0/1 Loss: ", post_shuffle)
 
+# classified_data = classifier.classify_db(temp_attr_headers, repaired_db, 0)
 
-print("\nFinished.")
+# print(classified_data)
+
+# print("\n\nRunning calc_prob_of_response():")
+# probs = classifier.calc_prob_of_response(classified_data)
+# print('\n\nprobs:\n')
+# print(probs)
+# print('\n\nprobs Products:\n')
+# print(classifier.predict(probs,['a2'],temp_attr_headers,repaired_db[0]))
+
+wb = Workbook()
+sheet = wb.add_sheet("FUCK, SHIT.")
+
+sheet.write(0, 0, "PRECISION")
+sheet.write(0, 1, "RECALL")
+sheet.write(0, 2, "0/1 LOSS")
+
+binned_data = classifier.separate_data(db.get_attr(),db.get_data())
+
+precision_list = []
+recall_list = []
+loss_list = []
+
+for i in range(1,1001):
+    precision, recall, loss = k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, True)
+    
+    precision_list.append(precision)
+    recall_list.append(recall)
+    loss_list.append(loss)
+    
+wb.save('rand_results_'+str(selected_database)+'.xls')
+
+print("\nPRECISION:")
+print("Mean:", statistics.mean(precision_list))
+print("Standard deviation:", statistics.stdev(precision_list))
+
+print("\nRECALL:")
+print("Mean:", statistics.mean(recall_list))
+print("Standard deviation:", statistics.stdev(recall_list))
+
+print("\nLOSS:")
+print("Mean:", statistics.mean(loss_list))
+print("Standard deviation:", statistics.stdev(loss_list))
+
+print("FINISHED.")
+
+# Use this site to plot stuff: https://www.essycode.com/distribution-viewer/

### 2019-09-13 paper/paper.tex
paper progress

@@
 We ran this algorithm on the original versions of each data set, and then introduced noise to each of the data sets by shuffling attribute values among 10\% of the values, and ran the algorithm of the five shuffled versions of the data.
-We hypothesized that we would acheive
+\\ \\
+% Hypotheses
+Our hypotheses for each data set are as follows: \\
+
+\textit{Breast Cancer Wisconsin:} This data set is comprised of 9 quantitative variables, and each data example can be classified as either benign or malignant.
+We hypothesized that, given that there are only two possible classifications, that we will acheive no less than 85\% accuracy (i.e.
+a 0-1 loss score of 0.75) on our unshuffled data.
+\\ \\
+\textit{Glass:} This data set is comprised of 7 quantitative variables, and each data example can be classified as one of 7 possible glass types: building\_windows\_float\_processed, building\_windows\_non\_float\_processed, vehicle\_windows\_float\_processed, vehicle\_windows\_non\_float\_processed, containers, tableware, or headlamps.
+We hypothesize that we will achieve no less that 65\% accuracy for this data set, given that there are 7 potential classes.
+\\ \\
+\textit{Iris:} This dataset is comprised of 4 quantitative variables. Each data example can be classified as one of three different flower types. We are predicting approximately 75\% accuracy. \\ \\
+\textit{Soybean:} This dataset is comprised of 35 attributes, and each data example can be classified as one of four different classifiers. We hypothesize 70\% accuracy for this data set. \\ \\
+\textit{Voting Records:} This data set is comprised \\
 

### 2019-09-13 paper/paper.tex
more paper progress

@@
 
-A brief, one paragraph abstract summarizing the results of the experiments
+In this assignment, we implemented the naive Bayes prediction model on 5 data sets.
+We utilized 10-fold cross-validation to test our implementation and measured accuracy with two loss functions: 0-1 loss, and Precision/Recall.
 
@@
 \begin{keywords}
-    Keywords, Go, Here
+    Bayes, 0-1 Loss, Precision/Recall, 
 %   Bayesian Networks, Mixture Models, Chow-Liu Trees
@@
 % Hypotheses
-Our hypotheses for each data set are as follows: \\
-
+Our hypotheses for each data set are as follows: \\ \\
 \textit{Breast Cancer Wisconsin:} This data set is comprised of 9 quantitative variables, and each data example can be classified as either benign or malignant.
-We hypothesized that, given that there are only two possible classifications, that we will acheive no less than 85\% accuracy (i.e.
+We hypothesized that, given that there are only two possible classifications, that we will achieve no less than 85\% accuracy (i.e.
 a 0-1 loss score of 0.75) on our unshuffled data.
+We think that the shuffled breast cancer data will be no more than 3\% less accurate.
 \\ \\
 \textit{Glass:} This data set is comprised of 7 quantitative variables, and each data example can be classified as one of 7 possible glass types: building\_windows\_float\_processed, building\_windows\_non\_float\_processed, vehicle\_windows\_float\_processed, vehicle\_windows\_non\_float\_processed, containers, tableware, or headlamps.
-We hypothesize that we will achieve no less that 65\% accuracy for this data set, given that there are 7 potential classes.
+We hypothesize that we will achieve no less that 65\% accuracy (0-1 loss of 0.65) for the unshuffled data, given that there are 7 potential classes.
+The shuffled data, we predict, will be no more than 5\% less accurate than the shuffled data.\\ \\
+\textit{Iris:} This dataset is comprised of 4 quantitative variables.
+Each data example can be classified as one of three different flower types.
+We are predicting approximately 75\% (0-1 loss of 0.75) accuracy.
 \\ \\
-\textit{Iris:} This dataset is comprised of 4 quantitative variables. Each data example can be classified as one of three different flower types. We are predicting approximately 75\% accuracy. \\ \\
-\textit{Soybean:} This dataset is comprised of 35 attributes, and each data example can be classified as one of four different classifiers. We hypothesize 70\% accuracy for this data set. \\ \\
-\textit{Voting Records:} This data set is comprised \\
+\textit{Soybean:} This dataset is comprised of 35 attributes, and each data example can be classified as one of four different classifiers.
+We hypothesize 70\% accuracy (0-1 loss of 0.7) for this unshuffled data.
+For the shuffled data we are predicting the accuracy to be approximately 3\% less accurate.\\ \\
+\textit{Voting Records:} This data set is comprised 16 categorical attributes, and each example may be classified as either republican or democrat.
+We are hypothesizing approximately 85\% accuracy (0-1 loss of 0.85) for this dataset.
+We are predicting that the shuffled voting-record data should no more than 3\% less accurate than the shuffled data.\\
 

### 2019-09-13 paper/paper.tex
more paper progress

@@
 \begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
-
 In this assignment, we implemented the naive Bayes prediction model on 5 data sets.
@@
 \\ \\
-\textit{Glass:} This data set is comprised of 7 quantitative variables, and each data example can be classified as one of 7 possible glass types: building\_windows\_float\_processed, building\_windows\_non\_float\_processed, vehicle\_windows\_float\_processed, vehicle\_windows\_non\_float\_processed, containers, tableware, or headlamps.
+\textit{Glass:} This data set is comprised of 7 quantitative variables, and each data example can be classified as one of 7 possible glass types: building\_windows\_float\_processed, building\_windows\_non-float\_processed, vehicle\_windows\_float\_processed, vehicle\_windows non float processed, containers, tableware, or headlamps.
 We hypothesize that we will achieve no less that 65\% accuracy (0-1 loss of 0.65) for the unshuffled data, given that there are 7 potential classes.
@@
 % Shuffling(?)
+We implemented our prediction algorithm on the original version of each data set, and also introduced noise to each data set by randomly selecting 10\% of each data set and the shuffling attribute values.
+We then ran our algorithm on these shuffled versions of each data set.
 %K-Fold Cross Validation

### 2019-09-13 paper/paper.tex
Merge

@@
 \begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
-In this assignment, we implemented the naive Bayes prediction model on 5 data sets.
-We utilized 10-fold cross-validation to test our implementation and measured accuracy with two loss functions: 0-1 loss, and Precision/Recall.
+
+In this assignment, we implemented the naive Bayes machine learning algorithm [3] on 5 data sets.
+We utilized 10-fold cross-validation to test our implementation and measured accuracy with two loss functions: 0-1 Loss, and Precision/Recall [1].
 
@@
 \begin{keywords}
-    Bayes, 0-1 Loss, Precision/Recall, 
+    naive Bayes, 0-1 Loss, Precision/Recall, cross-validation, 
 %   Bayesian Networks, Mixture Models, Chow-Liu Trees
@@
 \section{Introduction}
-The naive Bayes classification model is a simple model for predicting data classification.
-In this assignment, we implemented this probabilistic model on multiple real-world datasets.
+The naive Bayes classification model [3] is a simple model for predicting data classification.
+In this assignment, we implemented this probabilistic model on multiple real-world data sets.
 We validated our implementation of the algorithm with 10-fold cross-validation and measured the performance of our implementation with two loss functions: 0-1 Loss, and Precision/Recall.
@@
 We hypothesized that, given that there are only two possible classifications, that we will achieve no less than 85\% accuracy (i.e.
-a 0-1 loss score of 0.75) on our unshuffled data.
+a 0-1 Loss score of 0.75) on our un-shuffled data.
 We think that the shuffled breast cancer data will be no more than 3\% less accurate.
 \\ \\
-\textit{Glass:} This data set is comprised of 7 quantitative variables, and each data example can be classified as one of 7 possible glass types: building\_windows\_float\_processed, building\_windows\_non-float\_processed, vehicle\_windows\_float\_processed, vehicle\_windows non float processed, containers, tableware, or headlamps.
-We hypothesize that we will achieve no less that 65\% accuracy (0-1 loss of 0.65) for the unshuffled data, given that there are 7 potential classes.
+\textit{Glass:} This data set is comprised of 7 quantitative variables, and each data example can be classified as one of 7 possible glass types: building\_windows\_float\_processed, building\_windows\_non\_float\_processed, vehicle\_windows\_float\_processed, vehicle\_windows\_non- \\ \_float\_processed, containers, tableware, or headlamps.
+We hypothesize that we will achieve no less that 65\% accuracy (0-1 Loss of 0.65) for the un-shuffled data, given that there are 7 potential classes.
 The shuffled data, we predict, will be no more than 5\% less accurate than the shuffled data.\\ \\
-\textit{Iris:} This dataset is comprised of 4 quantitative variables.
+\textit{Iris:} This data set is comprised of 4 quantitative variables.
 Each data example can be classified as one of three different flower types.
-We are predicting approximately 75\% (0-1 loss of 0.75) accuracy.
+We are predicting approximately 75\% (0-1 Loss of 0.75) accuracy.
 \\ \\
-\textit{Soybean:} This dataset is comprised of 35 attributes, and each data example can be classified as one of four different classifiers.
-We hypothesize 70\% accuracy (0-1 loss of 0.7) for this unshuffled data.
+\textit{Soybean:} This data set is comprised of 35 attributes, and each data example can be classified as one of four different classifiers.
+We hypothesize 70\% accuracy (0-1 Loss of 0.7) for this un-shuffled data.
 For the shuffled data we are predicting the accuracy to be approximately 3\% less accurate.\\ \\
 \textit{Voting Records:} This data set is comprised 16 categorical attributes, and each example may be classified as either republican or democrat.
-We are hypothesizing approximately 85\% accuracy (0-1 loss of 0.85) for this dataset.
+We are hypothesizing approximately 85\% accuracy (0-1 Loss of 0.85) for this dataset.
 We are predicting that the shuffled voting-record data should no more than 3\% less accurate than the shuffled data.\\
@@
 % Separating and classifying data
-To properly implement naive Bayes on the 5 data sets, we first needed to properly separate and classify each data set.
+To properly implement naive Bayes [3] on the 5 data sets, we first needed to properly separate and classify each data set.
 Each data set needed to be separated by class, and then the count and probability of each attribute value for each class needed to be computed.
@@
 "Machine Learning for Sequential Data: A Review." Lecture Notes in Computer Science Structural, Syntactic, and Statistical Pattern Recognition, 2002, pp.
-15-30., doi:10.1007/3-540-70659-32.}
-
-% \acks{We would like to acknowledge support for this project
-% from the National Science Foundation (NSF grant IIS-9988642)
-% and the Multidisciplinary Research Program of the Department
-% of Defense (MURI N00014-00-1-0637). }
-
-% Manual newpage inserted to improve layout of sample file - not
-% needed in general before appendices/bibliography.
-
-\newpage
-
-\appendix
-\section*{Appendix A.}
-\label{app:theorem}
-
-% Note: in this sample, the section number is hard-coded in. Following
-% proper LaTeX conventions, it should properly be coded as a reference:
-
-%In this appendix we prove the following theorem from
-%Section~\ref{sec:textree-generalization}:
-
-In this appendix we prove the following theorem from
-Section~6.2:
-
-\noindent
-{\bf Theorem} {\it Let $u,v,w$ be discrete variables such that $v, w$ do
-not co-occur with $u$ (i.e., $u\neq0\;\Rightarrow \;v=w=0$ in a given
-dataset $\dataset$). Let $N_{v0},N_{w0}$ be the number of data points for
-which $v=0, w=0$ respectively, and let $I_{uv},I_{uw}$ be the
-respective empirical mutual information values based on the sample
-$\dataset$. Then
-\[
-	N_{v0} \;>\; N_{w0}\;\;\Rightarrow\;\;I_{uv} \;\leq\;I_{uw}
-\]
-with equality only if $u$ is identically 0.} \hfill\BlackBox
-
-\noindent
-{\bf Proof}. We use the notation:
-\[
-P_v(i) \;=\;\frac{N_v^i}{N},\;\;\;i \neq 0;\;\;\;
-P_{v0}\;\equiv\;P_v(0)\; = \;1 - \sum_{i\neq 0}P_v(i).
-\]
-These values represent the (empirical) probabilities of $v$
-taking value $i\neq 0$ and 0 respectively.  Entropies will be denoted
-by $H$. We aim to show that $\fracpartial{I_{uv}}{P_{v0}} < 0$....\\
-
-{\noindent \em Remainder omitted in this sample. See http://www.jmlr.org/papers/ for full paper.}
-
-\vskip 0.2in
-\bibliography{sample}
+15-30., doi:10.1007/3-540-70659-32.
+\\ \\
+3. Nédellec, Claire, and Céline Rouveirol, editors. “Machine Learning: ECML-98.” Lecture Notes in Computer Science, Springer Berlin Heidelberg, 1998. pp. 1-2., doi:10.1007/bfb0026664.}
 

### 2019-09-13 src/main.py

@@ -9,8 +9,6 @@ import process_data
 import classifier
 import k_fold_cross_validation
 from path_manager import pathManager as pm
-import xlwt
-from xlwt import Workbook
 import statistics
 
 # Asks for user to select a database from a list presented from current database collection directory.
@@ -93,13 +91,6 @@ print("0/1 Loss: ", post_shuffle)
 # print('\n\nprobs Products:\n')
 # print(classifier.predict(probs,['a2'],temp_attr_headers,repaired_db[0]))
 
-wb = Workbook()
-sheet = wb.add_sheet("FUCK, SHIT.")
-
-sheet.write(0, 0, "PRECISION")
-sheet.write(0, 1, "RECALL")
-sheet.write(0, 2, "0/1 LOSS")
-
 binned_data = classifier.separate_data(db.get_attr(),db.get_data())
 
 precision_list = []
@@ -113,8 +104,6 @@ for i in range(1,1001):
     recall_list.append(recall)
     loss_list.append(loss)
     
-wb.save('rand_results_'+str(selected_database)+'.xls')
-
 print("\nPRECISION:")
 print("Mean:", statistics.mean(precision_list))
 print("Standard deviation:", statistics.stdev(precision_list))

### 2019-09-13 paper/paper.tex
Auto stash before merge of "master" and "origin/master"
Paper Updates

@@
 \usepackage{amsmath}
-
 % Definitions of handy macros can go here
@@
 \section{Results}
+\begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
+    \centering
+    \begin{minipage}[b]{0.7\textwidth}
+      \includegraphics[width=\textwidth]{01_loss_graph.png}
+      \caption{Average 0/1 Loss for \emph{Iris} (over 1,000 iterations)}
+    \end{minipage}
+    \hfill
+    \begin{minipage}[b]{0.4\textwidth}
+      \includegraphics[width=\textwidth]{precision_graph.png}
+      \caption{Average Precision for \emph{Iris} (over 1,000 iterations)}
+    \end{minipage}
+    \hfill
+    \begin{minipage}[b]{0.4\textwidth}
+        \includegraphics[width=\textwidth]{recall_graph.png}
+        \caption{Average Recall for \emph{Iris} (over 1,000 iterations)}
+    \end{minipage}
+\end{figure}
+
+To construct these graphs, we ran 1,000 iterations of 10-fold cross-validation and found the average for the 0-1 Loss, precision, and recall against the Iris database.
+For the graph relating to Iris' recall over 1,000 iterations of 10-fold cross-validation, we are 95\% confident that the true recall for our naive Bayes algorithm's ability to classify test data is between 0.359 and 0.386 via a 95\% confidence interval.
+Regarding 0-1 Loss (the proportion of correct guesses by the naive Bayes algorithm), we are 95\% confident that the true 0-1 Loss for our naive Bayes algorithm's ability to classify test data is between 0.884 and 0.956 via a 95\% confidence interval.
+Finally, regarding precision, we are 95\% confident that the true precision for our naive Bayes algorithm's ability to classify test data is between 0.394 and 0.405 via a 95\% confidence interval.
 

### 2019-09-13 paper/paper.tex
Updated formatting and added a lot.

@@
 \section{Our Approach}
-% Preprocessing
+\subsection{Handling missing data}
+ We opted to not remove data with missing values that occurs in low quantities, as given the already-small size of the data sets we are working with for this assignment, we thought it best to retain as much data as possible for training purposes.
 
-% Separating and classifying data
+Rather, we decided to handle missing attribute values by replacing them with attributes selected randomly from a bootstrap distribution generated from all other data points in the database of the same attribute type that do not contain missing values.
+
+It is also worth noting that we do not hard code the symbol used for checking for missing values, but rather the missing value symbol is determined in the configuration '.attr' file that is unique for each database.
+It was handled in this manner due to inconsistencies between data sets with respect to symbols representing missing data.
+
+\subsection{Handling information about Attributes}
+Due to the fact that the databases had some uniqueness about them, rather than changing them directly to fit a generic format, we found it best to add a short and sweet configuration file for each database that would determine certain values when running our code.
+This way, we can both easily customize our parameters, and not have to rely on something primitive like command line user input.
+
+The configuration file being referred to is the '.attr' file that exists in the directory of each database.
+it is required that the respective attribute configuration file ('.attr' file) has the same prefix as the '.data' file for the database in order to function, as our code base looks for the '.data' file in the database directory specified, and then uses the prefix of the file name when locating the attribute file.
+
+The attribute file contains things like the column headers, column index of the attribute we want to classify, a list of indexes of the parameters used for classification, and finally, the last line is what will be used as the 'missing symbol', which is referenced in section (4.1).
+When running the program, these values are loaded in after the user selects a database from the list presented, and used accordingly.
+
+\subsection{Shuffling/Applying Noise}
+We implemented our prediction algorithm on the original version of each data set, and also introduced noise to each data set by randomly selecting 10\% of each data set and the shuffling attribute values.
+We then ran our algorithm on these shuffled versions of each data set.
+
+\subsection{Separating and classifying data}
 To properly implement naive Bayes [3] on the 5 data sets, we first needed to properly separate and classify each data set.
@@
 \\ \\
-% Shuffling(?)
-We implemented our prediction algorithm on the original version of each data set, and also introduced noise to each data set by randomly selecting 10\% of each data set and the shuffling attribute values.
-We then ran our algorithm on these shuffled versions of each data set.
-%K-Fold Cross Validation
+
+\subsection{K-Fold Cross Validation}
 We tested our algorithm's implementation using 10-fold cross-validation.
@@
 \\ \\
-% Loss functions
+
+\subsection{Loss functions}
 To assess the performance of our class prediction algorithm, we implemented two loss functions: Precision/Recall, and 0-1 Loss.
@@
 Accuracy is then defined as the percentage of 0's returned [2].\\ \\
-% Loss function 1: Precision Recall
+
+\subsection{Loss function 1: Precision Recall}
 The Precision/Recall loss function computes two values, known as precision and recall, to measure the performance of our class prediction algorithm.
@@
 
+The graphs shown are of the normal distribution of the values obtains from our loss functions for the iris data set, with 10\% noise applied.
+
 To construct these graphs, we ran 1,000 iterations of 10-fold cross-validation and found the average for the 0-1 Loss, precision, and recall against the Iris database.

### 2019-09-13 paper/paper.tex
updated abstract and over all goal

@@
 In this assignment, we implemented the naive Bayes machine learning algorithm [3] on 5 data sets.
-We utilized 10-fold cross-validation to test our implementation and measured accuracy with two loss functions: 0-1 Loss, and Precision/Recall [1].
+We utilized 10-fold cross-validation to test our implementation and measured difference in accuracy between the average accuracy returned by the cross-validation of the original data set and the average accuracy returned by the cross-validation of the data set with 10\% noise applied, using two loss functions: 0-1 Loss, and Precision/Recall [1].
 
@@
 We ran this algorithm on the original versions of each data set, and then introduced noise to each of the data sets by shuffling attribute values among 10\% of the values, and ran the algorithm of the five shuffled versions of the data.
+So now we want to know how the noise introduced via shuffling will affect our accuracy.
 \\ \\
@@
 
-\subsection{Shuffling/Applying Noise}
-We implemented our prediction algorithm on the original version of each data set, and also introduced noise to each data set by randomly selecting 10\% of each data set and the shuffling attribute values.
-We then ran our algorithm on these shuffled versions of each data set.
-
 \subsection{Separating and classifying data}
@@
 \\ \\
+
+\subsection{Shuffling/Applying Noise}
+
+In addition to implementing our prediction algorithm for the plain version of each data set, we also ran it with a 10\% noise modifier applied to the training data set in order to try and grasp how noise might affect the naive bayes machine learning algorithm.
+
+We implemented our prediction algorithm on the original version of each data set, and also introduced noise to each data set by randomly selecting 10\% of each data set and the shuffling attribute values.
+We then ran our algorithm on these shuffled versions of each data set.
 

### 2019-09-13 paper/paper.tex
More better formattinger

@@
 So now we want to know how the noise introduced via shuffling will affect our accuracy.
-\\ \\
-% Hypotheses
-Our hypotheses for each data set are as follows: \\ \\
-\textit{Breast Cancer Wisconsin:} This data set is comprised of 9 quantitative variables, and each data example can be classified as either benign or malignant.
+\\
+\section{Hypotheses}
+
+\subsection{Breast Cancer Wisconsin} This data set is comprised of 9 quantitative variables, and each data example can be classified as either benign or malignant.
 We hypothesized that, given that there are only two possible classifications, that we will achieve no less than 85\% accuracy (i.e.
@@
 We think that the shuffled breast cancer data will be no more than 3\% less accurate.
-\\ \\
-\textit{Glass:} This data set is comprised of 7 quantitative variables, and each data example can be classified as one of 7 possible glass types: building\_windows\_float\_processed, building\_windows\_non\_float\_processed, vehicle\_windows\_float\_processed, vehicle\_windows\_non- \\ \_float\_processed, containers, tableware, or headlamps.
+\subsection{Glass} This data set is comprised of 7 quantitative variables, and each data example can be classified as one of 7 possible glass types: building\_windows\_float\_processed, building\_windows\_non\_float\_processed, vehicle\_windows\_float\_processed, vehicle\_windows\_non- \\ \_float\_processed, containers, tableware, or headlamps.
 We hypothesize that we will achieve no less that 65\% accuracy (0-1 Loss of 0.65) for the un-shuffled data, given that there are 7 potential classes.
-The shuffled data, we predict, will be no more than 5\% less accurate than the shuffled data.\\ \\
-\textit{Iris:} This data set is comprised of 4 quantitative variables.
+The shuffled data, we predict, will be no more than 5\% less accurate than the shuffled data.
+\subsection{Iris} This data set is comprised of 4 quantitative variables.
 Each data example can be classified as one of three different flower types.
 We are predicting approximately 75\% (0-1 Loss of 0.75) accuracy.
-\\ \\
-\textit{Soybean:} This data set is comprised of 35 attributes, and each data example can be classified as one of four different classifiers.
+\subsection{Soybean} This data set is comprised of 35 attributes, and each data example can be classified as one of four different classifiers.
 We hypothesize 70\% accuracy (0-1 Loss of 0.7) for this un-shuffled data.
-For the shuffled data we are predicting the accuracy to be approximately 3\% less accurate.\\ \\
-\textit{Voting Records:} This data set is comprised 16 categorical attributes, and each example may be classified as either republican or democrat.
+For the shuffled data we are predicting the accuracy to be approximately 3\% less accurate.
+\subsection{Voting Records} This data set is comprised 16 categorical attributes, and each example may be classified as either republican or democrat.
 We are hypothesizing approximately 85\% accuracy (0-1 Loss of 0.85) for this dataset.

### 2019-09-13 paper/paper.tex
Generic hypothesis implemented

@@
 
-\subsection{Breast Cancer Wisconsin} This data set is comprised of 9 quantitative variables, and each data example can be classified as either benign or malignant.
-We hypothesized that, given that there are only two possible classifications, that we will achieve no less than 85\% accuracy (i.e.
-a 0-1 Loss score of 0.75) on our un-shuffled data.
-We think that the shuffled breast cancer data will be no more than 3\% less accurate.
-\subsection{Glass} This data set is comprised of 7 quantitative variables, and each data example can be classified as one of 7 possible glass types: building\_windows\_float\_processed, building\_windows\_non\_float\_processed, vehicle\_windows\_float\_processed, vehicle\_windows\_non- \\ \_float\_processed, containers, tableware, or headlamps.
-We hypothesize that we will achieve no less that 65\% accuracy (0-1 Loss of 0.65) for the un-shuffled data, given that there are 7 potential classes.
-The shuffled data, we predict, will be no more than 5\% less accurate than the shuffled data.
-\subsection{Iris} This data set is comprised of 4 quantitative variables.
-Each data example can be classified as one of three different flower types.
-We are predicting approximately 75\% (0-1 Loss of 0.75) accuracy.
-\subsection{Soybean} This data set is comprised of 35 attributes, and each data example can be classified as one of four different classifiers.
-We hypothesize 70\% accuracy (0-1 Loss of 0.7) for this un-shuffled data.
-For the shuffled data we are predicting the accuracy to be approximately 3\% less accurate.
-\subsection{Voting Records} This data set is comprised 16 categorical attributes, and each example may be classified as either republican or democrat.
-We are hypothesizing approximately 85\% accuracy (0-1 Loss of 0.85) for this dataset.
-We are predicting that the shuffled voting-record data should no more than 3\% less accurate than the shuffled data.\\
+\subsection{Breast Cancer Wisconsin} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
+$H_0 : \mu \geq m$
+
+\subsection{Glass} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
+$H_0 : \mu \geq m$
+
+\subsection{Iris} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
+$H_0 : \mu \geq m$
+
+\subsection{Soybean} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
+$H_0 : \mu \geq m$
+
+\subsection{Voting Records} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
+$H_0 : \mu \geq m$
 

### 2019-09-13 paper/paper.tex
'variance' now included :]

@@
 
-\subsection{Breast Cancer Wisconsin} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
+\subsection{Breast Cancer Wisconsin} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified Breast Cancer Wisconsin data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the Breast Cancer Wisconsin data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
 $H_0 : \mu \geq m$
 
-\subsection{Glass} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
+\subsection{Glass} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified Glass data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the Glass data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
 $H_0 : \mu \geq m$
 
-\subsection{Iris} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
+\subsection{Iris} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified Iris data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the Iris data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
 $H_0 : \mu \geq m$
 
-\subsection{Soybean} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
+\subsection{Soybean} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified Soybean data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the Soybean data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
 $H_0 : \mu \geq m$
 
-\subsection{Voting Records} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
+\subsection{Voting Records} The null hypothesis assumes the difference between the true mean of the accuracy of the unmodified Voting Records data set obtained from 10-fold cross validation and the true mean of the generated accuracy values from the Voting Records data set with 10\% randomized noise applied to it obtained from 10-fold cross validation is equal to or greater than 0.\\\\
 $H_0 : \mu \geq m$

### 2019-09-13 paper/paper.tex
Added subsection for convertsion from discrete to continuous data
-NEEDS TO BE FILLED IN STILL
Added subsection for loss function
Added subsections for additional Conclusions
-Also need to dump results in relevant section.
Filled in subsection for converting data type

@@
 
+\subsection{Converting continuous (discrete) data into categorical}
+
+Since we can’t really deal with continuous attributes when using the Naive Bayes algorithm, we have to convert any continuous (quantitative) data to a categorical format.
+
+We do so on a column by column basis, beginning with checking if the column contains quantitative data or not by seeing if it can be converted to a float.
+If any one of the elements of that column can’t be converted, it implies the column is of categorical typing.
+
+Once we find  column that we know contains discrete data, we can begin converting it using equal width binning.
+The equal width binning method finds the smallest and largest values of the quantitative data, subtracts the new found max from the min, and divides the result by the amount of bins.
+The result is the width of each bin!
+
+From there we simply sort the discrete data into their respective bins in the form of the entire row from the database via the pop() function, and then goes on to convert every value in each respective bin to the value range it belongs to.
+Value range being the bin bounds.
+Then the rows are simply recompiled into the database, returned, and repeats this cycle for each column.
+
+Side note: It is fairly obvious we didn't choose this method for it’s efficiency, but rather its simplicity, and consistency.
+
 \subsection{Separating and classifying data}
@@
 
+\subsection{Loss function 2: 0-1 Loss}
+-TODO: describe Loss function in a similar function to precision recall.
+
 \section{Results}
+
+\section{Conclusions}
+\subsection{Breast Cancer Wisconsin}
+\subsection{Glass}
+\subsection{Iris}
 \begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
@@
 
+\subsection{Soybean}
+\subsection{Voting Records}
+
 % Acknowledgements should go at the end, before appendices and references
-
 \acks{1.

### 2019-09-13 src/main.py
main now spits out things in terms of difference

@@ -69,16 +69,16 @@ db.set_data(repaired_db)
 
 process_data.convert(db.get_data())
 
-binned_data = classifier.separate_data(db.get_attr(),db.get_data())
+# binned_data = classifier.separate_data(db.get_attr(),db.get_data())
 
-print('\n \n Pre-shuffle')
-print('---------------------')
-pre_shuffle = k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, False)
-print("0/1 Loss: ", pre_shuffle)
-print('\n \n Post-shuffle')
-print('---------------------')
-post_shuffle = k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, True)
-print("0/1 Loss: ", post_shuffle)
+# print('\n \n Pre-shuffle')
+# print('---------------------')
+# pre_shuffle = k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, False)
+# print("0/1 Loss: ", pre_shuffle)
+# print('\n \n Post-shuffle')
+# print('---------------------')
+# post_shuffle = k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, True)
+# print("0/1 Loss: ", post_shuffle)
 
 # classified_data = classifier.classify_db(temp_attr_headers, repaired_db, 0)
 
@@ -93,6 +93,9 @@ print("0/1 Loss: ", post_shuffle)
 
 binned_data = classifier.separate_data(db.get_attr(),db.get_data())
 
+# n stands for normal, as in before noise was applied.
+n_precision, n_recall, n_loss = k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, False)
+
 precision_list = []
 recall_list = []
 loss_list = []
@@ -100,9 +103,9 @@ loss_list = []
 for i in range(1,1001):
     precision, recall, loss = k_fold_cross_validation.k_fold(10,binned_data[0],binned_data[1], db, True)
     
-    precision_list.append(precision)
-    recall_list.append(recall)
-    loss_list.append(loss)
+    precision_list.append(n_precision-precision)
+    recall_list.append(n_recall-recall)
+    loss_list.append(n_loss-loss)
     
 print("\nPRECISION:")
 print("Mean:", statistics.mean(precision_list))

### 2019-09-13 paper/paper.tex
DANA PUT HERE

@@
 Each data set needed to be separated by class, and then the count and probability of each attribute value for each class needed to be computed.
-Our approach for this was to create, for each dataset, an associative array, where each possible classifier was a key.
+Our approach for this was to create, for each data set, an associative array, where each possible classifier was a key.
 For each key, the corresponding values were each their own associative arrays, the keys of which were all the extant attribute values among that class.
@@
 -TODO: describe Loss function in a similar function to precision recall.
+TODO: DANA PUT HERE
 
 \section{Results}
+TODO: DANA PUT HERE
 
 \section{Conclusions}
+
 \subsection{Breast Cancer Wisconsin}
+
+\begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
+    \centering
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{bc-l-ms.png}
+        \includegraphics[width=\textwidth]{bc-l-ds.png}
+        \caption{Average difference between 0/1 Loss for normal data set and noise data set for \emph{Breast Cancer Wisconsin} (over 1,000 iterations)}
+    \end{minipage}
+    \hfill
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{bc-p-ms.png}
+        \includegraphics[width=\textwidth]{bc-l-ds.png}
+        \caption{Average difference between Precision for normal data set and noise data set for\emph{Breast Cancer Wisconsin} (over 1,000 iterations)}
+    \end{minipage}
+    \hfill
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{bc-r-ms.png}
+        \includegraphics[width=\textwidth]{bc-r-ds.png}
+        \caption{Average difference between Recall for normal data set and noise data set for \emph{Breast Cancer Wisconsin} (over 1,000 iterations)}
+    \end{minipage}
+\end{figure}
+
 \subsection{Glass}
+
+\begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
+    \centering
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{g-l-ms.png}
+        \includegraphics[width=\textwidth]{g-l-ds.png}
+        \caption{Average difference between 0/1 Loss for normal data set and noise data set for \emph{Glass} (over 1,000 iterations)}
+    \end{minipage}
+    \hfill
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{g-p-ms.png}
+        \includegraphics[width=\textwidth]{g-l-ds.png}
+        \caption{Average difference between Precision for normal data set and noise data set for\emph{Glass} (over 1,000 iterations)}
+    \end{minipage}
+    \hfill
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{g-r-ms.png}
+        \includegraphics[width=\textwidth]{g-r-ds.png}
+        \caption{Average difference between Recall for normal data set and noise data set for \emph{Glass} (over 1,000 iterations)}
+    \end{minipage}
+\end{figure}
+
 \subsection{Iris}
@@
     \centering
-    \begin{minipage}[b]{0.7\textwidth}
-      \includegraphics[width=\textwidth]{01_loss_graph.png}
-      \caption{Average 0/1 Loss for \emph{Iris} (over 1,000 iterations)}
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{iris-loss-ms.png}
+        \includegraphics[width=\textwidth]{densityfunc-iris-loss.png}
+        \caption{Average difference between 0/1 Loss for normal data set and noise data set for \emph{Iris} (over 1,000 iterations)}
     \end{minipage}
     \hfill
-    \begin{minipage}[b]{0.4\textwidth}
-      \includegraphics[width=\textwidth]{precision_graph.png}
-      \caption{Average Precision for \emph{Iris} (over 1,000 iterations)}
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{iris-precs-ms.png}
+        \includegraphics[width=\textwidth]{densityfunction-iris-precision.png}
+        \caption{Average difference between Precision for normal data set and noise data set for\emph{Iris} (over 1,000 iterations)}
     \end{minipage}
     \hfill
-    \begin{minipage}[b]{0.4\textwidth}
-        \includegraphics[width=\textwidth]{recall_graph.png}
-        \caption{Average Recall for \emph{Iris} (over 1,000 iterations)}
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{iris-recall-ms.png}
+        \includegraphics[width=\textwidth]{densityfunc-iris-recall.png}
+        \caption{Average difference between Recall for normal data set and noise data set for \emph{Iris} (over 1,000 iterations)}
     \end{minipage}
@@
 \subsection{Soybean}
+
+\begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
+    \centering
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{soybean-l-ms.png}
+        \includegraphics[width=\textwidth]{soybean-l-df.png}
+        \caption{Average difference between 0/1 Loss for normal data set and noise data set for \emph{Soybean} (over 1,000 iterations)}
+    \end{minipage}
+    \hfill
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{soybean-p-ms.png}
+        \includegraphics[width=\textwidth]{soybean-l-df.png}
+        \caption{Average difference between Precision for normal data set and noise data set for\emph{Soybean} (over 1,000 iterations)}
+    \end{minipage}
+    \hfill
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{soybean-r-ms.png}
+        \includegraphics[width=\textwidth]{soybean-r-df.png}
+        \caption{Average difference between Recall for normal data set and noise data set for \emph{Soybean} (over 1,000 iterations)}
+    \end{minipage}
+\end{figure}
+
 \subsection{Voting Records}
+
+\begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
+    \centering
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{vr-l-ms.png}
+        \includegraphics[width=\textwidth]{vr-l-df.png}
+        \caption{Average difference between 0/1 Loss for normal data set and noise data set for \emph{Voting Records} (over 1,000 iterations)}
+    \end{minipage}
+    \hfill
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{vr-p-ms.png}
+        \includegraphics[width=\textwidth]{vr-p-df.png}
+        \caption{Average difference between Precision for normal data set and noise data set for\emph{Voting Records} (over 1,000 iterations)}
+    \end{minipage}
+    \hfill
+    \begin{minipage}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{vr-r-ms.png}
+        \includegraphics[width=\textwidth]{vr-r-df.png}
+        \caption{Average difference between Recall for normal data set and noise data set for \emph{Voting Records} (over 1,000 iterations)}
+    \end{minipage}
+\end{figure}
 

### 2019-09-13 paper/paper.tex
MORE

@@
 
+The graphs shown are of the difference between the normal distribution of the values obtains from our loss functions for the iris data set, and the averages of values obtains from our loss functions for the iris data set with a 10\% noise function applied.
+
 \subsection{Breast Cancer Wisconsin}
@@
     \begin{minipage}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{bc-l-ms.png}
-        \includegraphics[width=\textwidth]{bc-l-ds.png}
+        \includegraphics[width=\textwidth]{bs-l-ms.png}
+        \includegraphics[width=\textwidth]{bs-l-ds.png}
         \caption{Average difference between 0/1 Loss for normal data set and noise data set for \emph{Breast Cancer Wisconsin} (over 1,000 iterations)}
@@
     \begin{minipage}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{bc-p-ms.png}
-        \includegraphics[width=\textwidth]{bc-l-ds.png}
+        \includegraphics[width=\textwidth]{bs-p-ms.png}
+        \includegraphics[width=\textwidth]{bs-l-ds.png}
         \caption{Average difference between Precision for normal data set and noise data set for\emph{Breast Cancer Wisconsin} (over 1,000 iterations)}
@@
     \begin{minipage}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{bc-r-ms.png}
-        \includegraphics[width=\textwidth]{bc-r-ds.png}
+        \includegraphics[width=\textwidth]{bs-r-ms.png}
+        \includegraphics[width=\textwidth]{bs-r-ds.png}
         \caption{Average difference between Recall for normal data set and noise data set for \emph{Breast Cancer Wisconsin} (over 1,000 iterations)}
@@
 \end{figure}
-
-The graphs shown are of the normal distribution of the values obtains from our loss functions for the iris data set, with 10\% noise applied.
-
+TODO: Change up for difference!
 To construct these graphs, we ran 1,000 iterations of 10-fold cross-validation and found the average for the 0-1 Loss, precision, and recall against the Iris database.
-For the graph relating to Iris' recall over 1,000 iterations of 10-fold cross-validation, we are 95\% confident that the true recall for our naive Bayes algorithm's ability to classify test data is between 0.359 and 0.386 via a 95\% confidence interval.
-Regarding 0-1 Loss (the proportion of correct guesses by the naive Bayes algorithm), we are 95\% confident that the true 0-1 Loss for our naive Bayes algorithm's ability to classify test data is between 0.884 and 0.956 via a 95\% confidence interval.
-Finally, regarding precision, we are 95\% confident that the true precision for our naive Bayes algorithm's ability to classify test data is between 0.394 and 0.405 via a 95\% confidence interval.
+For the graph relating to Iris' recall over 1,000 iterations of 10-fold cross-validation, we are 95\% confident that the true recall for our naive Bayes algorithm's ability to classify test data is between 0.0272 and 0.180 via a 95\% confidence interval.
+Regarding 0-1 Loss (the proportion of correct guesses by the naive Bayes algorithm), we are 95\% confident that the true 0-1 Loss for our naive Bayes algorithm's ability to classify test data is between 0.0272 and 0.180 via a 95\% confidence interval.
+Finally, regarding precision, we are 95\% confident that the true precision for our naive Bayes algorithm's ability to classify test data is between 0.010 and 0.007 via a 95\% confidence interval.
 
@@
 \end{document}
+
+BACKUP: 
+To construct these graphs, we ran 1,000 iterations of 10-fold cross-validation and found the average for the 0-1 Loss, precision, and recall against the Iris database.
+For the graph relating to Iris' recall over 1,000 iterations of 10-fold cross-validation, we are 95\% confident that the true recall for our naive Bayes algorithm's ability to classify test data is between 0.359 and 0.386 via a 95\% confidence interval.
+Regarding 0-1 Loss (the proportion of correct guesses by the naive Bayes algorithm), we are 95\% confident that the true 0-1 Loss for our naive Bayes algorithm's ability to classify test data is between 0.884 and 0.956 via a 95\% confidence interval.
+Finally, regarding precision, we are 95\% confident that the true precision for our naive Bayes algorithm's ability to classify test data is between 0.394 and 0.405 via a 95\% confidence interval.
